---
title: "AIUQ tutorial"
output: rmarkdown::html_vignette
author: "Yue He, Xubo Liu, Mengyang Gu"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{AIUQ tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette, we will demonstrate the core functionalities of the AIUQ package. These include estimating parameters and mean squared displacement(MSD) with associated uncertainties; simulating particle movements governed by various stochastic processes and generating corresponding intensity profiles to emulate microscopic images. More examples including the application of this package to real experimental data can be found on [GitHub](https://github.com/UncertaintyQuantification/AIUQ-R). 

We start by importing the AIUQ library.
```{r setup}
library(AIUQ)
```

## Example 1: Simulate BM and get estimated parameters using BM model

To illustrate the method, we simulate a data set using default values of the `simulation` class which corresponding to the Brownian Motion(BM). (`show()` prints the main parameters used in simulation.)
```{r,fig.height = 3.5, fig.width = 3.5}
set.seed(1)

sim_bm = simulation()
show(sim_bm)

## Plot simulated particle trajectory
plot_traj(sim_bm)
```

```{r,fig.height = 3.5, fig.width = 7}
par(mfrow=c(1,2))
## Plot intensity profile for different frames 
plot_intensity(sim_bm@intensity, sz=sim_bm@sz) #first frame 
plot_intensity(sim_bm@intensity, sz=sim_bm@sz,frame=10, color=T) #10th frame, color image
```

Next, we can estimate the MSD and other parameters with selected fitting model. 
```{r, fig.height = 3.5, fig.width = 7}
## AIUQ method: use BM as fitted model 
sam = SAM(sim_object=sim_bm, model_name='BM')
show(sam)

par(mfrow=c(1,2))
## Plot true MSD and estimated MSD
plot_MSD(object=sam, msd_truth=sam@msd_truth) #in log10 scale

## Plot intensity in reciprocal space 
plot_I_q_1 = matrix(sam@I_q[,1], sam@sz[1],sam@sz[2]) #first frame 
plot3D::image2D(abs(fftshift(plot_I_q_1)),main="intensity in reciprocal space")

```

User can select wavevector q range via AIUQ_thr or index_q. 
```{r}
sam = SAM(sim_object=sim_bm, AIUQ_thr=c(0.99,0.6)) 
#Note: Default model_name is "BM", it's ok to not specify this argument if want to fit with BM model 
show(sam)

sam = SAM(sim_object=sim_bm, index_q_AIUQ=5:50)
show(sam)
```

## Example 2: Simulate BM with user defined parameters and get estimated MSD with uncertainty
```{r, fig.height = 3.5, fig.width = 3.5}
set.seed(1)

## Simulation
sim_bm = simulation(sz=100,len_t=100,sigma_bm=0.5)
show(sim_bm)

## Plot simulated particle trajectory
plot_traj(sim_bm)
```

```{r, fig.height = 3.5, fig.width = 7}
## AIUQ method: fitting using BM model with uncertainty quantification 
sam = SAM(sim_object=sim_bm, uncertainty=T)
show(sam)

par(mfrow=c(1,2))
## Plot true MSD and estimated MSD with uncertainty 
plot_MSD(object=sam, msd_truth=sam@msd_truth) #in log10 scale 
plot_MSD(object=sam, msd_truth=sam@msd_truth,log10=F) #in real scale
```

## Example 3: Simulate OU process and get estimated parameters using OU model
```{r, fig.height = 3.5, fig.width = 7}
set.seed(1)

## Simulation
sim_ou = simulation(sigma_ou=4, model_name="OU")
show(sim_ou)

par(mfrow=c(1,2))
## Plot simulated particle trajectory
plot_traj(sim_ou)

## AIUQ method: fitting using OU model
sam_ou = SAM(sim_object=sim_ou, model_name=sim_ou@model_name) 
show(sam_ou)

## Plot true MSD and estimated MSD with uncertainty
plot_MSD(object=sam_ou, msd_truth=sam_ou@msd_truth) #in log10 scale
```

## Example 4: User defined MSD structure 
```{r}
set.seed(1)

## Simulation
sim_bm = simulation(sz=100,len_t=100,sigma_bm=0.5)
show(sim_bm)

## User defined MSD structure: function of parameters and 
#                                          vector of lag times 
msd_fn = function(param, d_input){
  MSD = param[1]*d_input+param[2]*d_input^2
}

# show MSD and MSD gradient with a simple example 
theta = c(2,1)
d_input = 0:10
model_name = "user_defined"
MSD_list = get_MSD_with_grad(theta=theta,d_input=d_input,model_name=model_name,
                             msd_fn=msd_fn)
MSD_list$msd

## AIUQ method: fitting using user_defined model 
sam = SAM(sim_object=sim_bm, model_name=model_name, msd_fn=msd_fn, num_param=2)
show(sam)
```
