---
title: Introduction to Allspice
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: true
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
body {
  text-align: justify;
}
p.caption {
  display: inline-block;
  padding-left: 0.5em;
  padding-right: 0.5em;
  border-color: #F4F4F4;
  border-width: 1px;
  border-style: solid;
  border-radius: 4px;
  background-color: #F6F6F6;
  text-align: justify;
}
div.caption {
  display: inline-block;
  padding-left: 0.5em;
  padding-right: 0.5em;
  border-color: #F4F4F4;
  border-width: 1px;
  border-style: solid;
  border-radius: 4px;
  background-color: #F6F6F6;
  text-align: justify;
}
h1 {
  margin-top: 1em;
  margin-bottom: 0.1em;
}
h2 {
  margin-top: 0.2em;
  margin-bottom: 0.1em;
}
</style>

**Author:** Ville-Petteri Mäkinen  
**Version:** `r packageVersion("Allspice")`

**Abstract:** Allspice is a lightweight machine learning tool that was
initially developed for RNA profiling of acute lymphoplastic leukemia,
but it can be used for any problem where multiple classes need
to be identified from multi-dimensional data. The classifier contains
optimized mean profiles for the classes (centroids) as observed in the
training data, and new samples are matched to these centroids using the
shortest Euclidean distance. Allspice produces both numerical and visual
output of the classification results and flags samples with mixed features
from multiple classes or atypical values.

**Citation:**  Ville-Petteri Mäkinen, Jacqueline Rehn, James Breen, David Yeung, Deborah L White (2022) Multi-cohort transcriptomic subtyping of B-cell acute lymphoblastic leukemia, Int J Mol Sci 2022, 23(9), 4574, https://doi.org/10.3390/ijms23094574 

**Resources:**  Additional assets were created from tissue-specific RNA-seq data from the Genotype-Tissue Expression Project v8 [Lonsdale J et al. Nat Genet 45, 580–585 (2013) https://doi.org/10.1038/ng.2653], from lymphoblastoid cell lines [Lappalainen et al. Nature 2013 September 26; 501(7468): 506–511. doi:10.1038/nature12531], from pediatric T-cell leukemia samples [Drobna-Śledzińska et al. ArrayExpress E-MTAB-11759, accessed 2022], and from 11 EPT and 134 T-cell ALL samples (South Australian Health and Medical Research Institute, 2022, unpublished).

<svg
   xmlns:dc="http://purl.org/dc/elements/1.1/"
   xmlns:cc="http://creativecommons.org/ns#"
   xmlns:rdf="http://www.w3.org/1999/02/22-rdf-syntax-ns#"
   xmlns:svg="http://www.w3.org/2000/svg"
   xmlns="http://www.w3.org/2000/svg"
   id="svg8"
   version="1.1"
   viewBox="0 0 171.97917 42.333334"
   height="160"
   width="650">
  <defs
     id="defs2">
    <marker
       style="overflow:visible"
       id="marker3621"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path3619" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker1319"
       style="overflow:visible">
      <path
         id="path1317"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2702"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2700" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2470"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2468" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker10633"
       style="overflow:visible">
      <path
         id="path10631"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker8705"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path8703" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker8577"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path8575" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker7895"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path7893" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker7273"
       style="overflow:visible">
      <path
         id="path7271"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker4786"
       style="overflow:visible">
      <path
         id="path4784"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker20325"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path20323" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker19827"
       style="overflow:visible">
      <path
         id="path19825"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker15111"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path15109" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker10869"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path10867" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker5520"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path5518" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker3450"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path3448" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2910"
       style="overflow:visible">
      <path
         id="path2908"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2792"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2790" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2680"
       style="overflow:visible">
      <path
         id="path2678"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2288"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2286" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2194"
       style="overflow:visible">
      <path
         id="path2192"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2106"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2104" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2006"
       style="overflow:visible">
      <path
         id="path2004"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker1260"
       style="overflow:visible">
      <path
         id="path1258"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker9062"
       style="overflow:visible">
      <path
         id="path9060"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker6764"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path6762" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker6184"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path6182" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker4074"
       style="overflow:visible">
      <path
         id="path4072"
         style="fill:#c837ab;fill-opacity:1;fill-rule:evenodd;stroke:#c837ab;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2646"
       style="overflow:visible">
      <path
         id="path2644"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker1794"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path1792" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker3621-9"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path3619-1" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker1319-2"
       style="overflow:visible">
      <path
         id="path1317-7"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2702-0"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2700-9" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2470-3"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2468-6" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker8705-0"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path8703-6" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker8577-2"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path8575-6" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker7895-1"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path7893-8" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker7273-7"
       style="overflow:visible">
      <path
         id="path7271-9"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker4786-20"
       style="overflow:visible">
      <path
         id="path4784-2"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker15111-5"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path15109-9" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker5520-9"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path5518-7" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker3450-3"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path3448-6" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2910-1"
       style="overflow:visible">
      <path
         id="path2908-29"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2792-3"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2790-1" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2680-9"
       style="overflow:visible">
      <path
         id="path2678-4"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2288-7"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2286-8" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2194-4"
       style="overflow:visible">
      <path
         id="path2192-5"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2106-0"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2104-3" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2006-6"
       style="overflow:visible">
      <path
         id="path2004-1"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker15111-3"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path15109-6" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker49830"
       style="overflow:visible">
      <path
         id="path49828"
         style="fill:#000000;fill-opacity:1;fill-rule:evenodd;stroke:#000000;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker49422"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#000000;fill-opacity:1;fill-rule:evenodd;stroke:#000000;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path49420" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker10633-0"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path10631-6" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker8705-7"
       style="overflow:visible">
      <path
         id="path8703-5"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker8577-3"
       style="overflow:visible">
      <path
         id="path8575-5"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker7895-6"
       style="overflow:visible">
      <path
         id="path7893-2"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker7273-9"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path7271-1" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker4786-2"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path4784-7" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker20325-0"
       style="overflow:visible">
      <path
         id="path20323-9"
         style="fill:#d35fbc;fill-opacity:1;fill-rule:evenodd;stroke:#d35fbc;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker19827-3"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="scale(-0.6)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path19825-2" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker15633"
       style="overflow:visible">
      <path
         id="path15631"
         style="fill:#5f8dd3;fill-opacity:1;fill-rule:evenodd;stroke:#5f8dd3;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker15111-36"
       style="overflow:visible">
      <path
         id="path15109-0"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker10869-6"
       style="overflow:visible">
      <path
         id="path10867-2"
         style="fill:#d35f5f;fill-opacity:1;fill-rule:evenodd;stroke:#d35f5f;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="scale(-0.6)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker5520-6"
       style="overflow:visible">
      <path
         id="path5518-1"
         style="fill:#808080;fill-opacity:1;fill-rule:evenodd;stroke:#808080;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker3450-8"
       style="overflow:visible">
      <path
         id="path3448-7"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2910-9"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2908-2" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2792-0"
       style="overflow:visible">
      <path
         id="path2790-2"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2680-3"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#de87aa;fill-opacity:1;fill-rule:evenodd;stroke:#de87aa;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2678-7" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2288-5"
       style="overflow:visible">
      <path
         id="path2286-9"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2194-2"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2192-2" />
    </marker>
    <marker
       orient="auto"
       refY="0"
       refX="0"
       id="marker2106-8"
       style="overflow:visible">
      <path
         id="path2104-9"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         transform="matrix(-0.3,0,0,-0.3,0.69,0)" />
    </marker>
    <marker
       style="overflow:visible"
       id="marker2006-7"
       refX="0"
       refY="0"
       orient="auto">
      <path
         transform="matrix(-0.3,0,0,-0.3,0.69,0)"
         d="M 8.7185878,4.0337352 -2.2072895,0.01601326 8.7185884,-4.0017078 c -1.7454984,2.3720609 -1.7354408,5.6174519 -6e-7,8.035443 z"
         style="fill:#55ddff;fill-opacity:1;fill-rule:evenodd;stroke:#55ddff;stroke-width:0.625;stroke-linejoin:round;stroke-opacity:1"
         id="path2004-3" />
    </marker>
    <g
       id="g16974">
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-0">
        <path
           style="stroke:none"
           d=""
           id="path16947" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-1">
        <path
           style="stroke:none"
           d="M 5.6875,-2.625 6.59375,0 h 1.25 L 4.765625,-8.75 h -1.4375 L 0.203125,0 h 1.1875 L 2.3125,-2.625 Z M 5.375,-3.5625 H 2.59375 l 1.4375,-3.984375 z m 0,0"
           id="path16950" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-2">
        <path
           style="stroke:none"
           d="M 1.828125,-8.75 H 0.8125 V 0 h 1.015625 z m 0,0"
           id="path16953" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-3">
        <path
           style="stroke:none"
           d=""
           id="path16956" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-4">
        <path
           style="stroke:none"
           d="m 5.25,-4.53125 c 0,-1.234375 -0.828125,-1.9375 -2.28125,-1.9375 -1.453125,0 -2.40625,0.75 -2.40625,1.921875 0,0.984375 0.5,1.453125 2,1.8125 l 0.921875,0.21875 c 0.703125,0.171875 0.984375,0.421875 0.984375,0.875 0,0.59375 -0.59375,1 -1.46875,1 -0.546875,0 -1,-0.15625 -1.25,-0.421875 C 1.59375,-1.25 1.53125,-1.421875 1.46875,-1.875 h -1.0625 c 0.046875,1.453125 0.859375,2.15625 2.515625,2.15625 1.578125,0 2.59375,-0.78125 2.59375,-2 0,-0.9375 -0.53125,-1.453125 -1.78125,-1.75 l -0.96875,-0.234375 c -0.8125,-0.1875 -1.15625,-0.453125 -1.15625,-0.890625 0,-0.59375 0.515625,-0.953125 1.328125,-0.953125 0.8125,0 1.234375,0.34375 1.265625,1.015625 z m 0,0"
           id="path16959" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-5">
        <path
           style="stroke:none"
           d="M 6.421875,-0.59375 C 6.3125,-0.5625 6.265625,-0.5625 6.203125,-0.5625 c -0.34375,0 -0.546875,-0.1875 -0.546875,-0.5 V -4.75 c 0,-1.125 -0.8125,-1.71875 -2.359375,-1.71875 -0.921875,0 -1.65625,0.265625 -2.078125,0.734375 -0.296875,0.328125 -0.421875,0.6875 -0.4375,1.3125 h 1 c 0.09375,-0.78125 0.546875,-1.125 1.484375,-1.125 0.90625,0 1.40625,0.34375 1.40625,0.9375 V -4.34375 C 4.65625,-3.90625 4.4375,-3.75 3.625,-3.640625 2.203125,-3.46875 1.984375,-3.421875 1.609375,-3.265625 0.875,-2.953125 0.5,-2.40625 0.5,-1.578125 0.5,-0.4375 1.296875,0.28125 2.5625,0.28125 3.359375,0.28125 4,0 4.703125,-0.640625 4.78125,0 5.09375,0.28125 5.734375,0.28125 c 0.21875,0 0.34375,-0.03125 0.6875,-0.109375 z m -1.75,-1.390625 c 0,0.34375 -0.09375,0.546875 -0.40625,0.828125 -0.40625,0.359375 -0.890625,0.5625 -1.484375,0.5625 -0.78125,0 -1.234375,-0.375 -1.234375,-1.015625 0,-0.65625 0.4375,-1 1.515625,-1.15625 1.0625,-0.140625 1.265625,-0.1875 1.609375,-0.34375 z m 0,0"
           id="path16962" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-6">
        <path
           style="stroke:none"
           d="M 0.84375,-6.28125 V 0 h 1 v -3.953125 c 0,-0.90625 0.671875,-1.640625 1.484375,-1.640625 0.734375,0 1.15625,0.453125 1.15625,1.265625 V 0 H 5.5 v -3.953125 c 0,-0.90625 0.65625,-1.640625 1.46875,-1.640625 0.734375,0 1.171875,0.46875 1.171875,1.265625 V 0 h 1 v -4.71875 c 0,-1.125 -0.640625,-1.75 -1.828125,-1.75 -0.828125,0 -1.34375,0.25 -1.921875,0.953125 -0.375,-0.671875 -0.875,-0.953125 -1.6875,-0.953125 -0.84375,0 -1.40625,0.3125 -1.9375,1.0625 v -0.875 z m 0,0"
           id="path16965" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-7">
        <path
           style="stroke:none"
           d="M 0.640625,2.609375 H 1.65625 V -0.65625 c 0.53125,0.640625 1.109375,0.9375 1.9375,0.9375 1.625,0 2.6875,-1.3125 2.6875,-3.3125 0,-2.109375 -1.03125,-3.4375 -2.703125,-3.4375 -0.859375,0 -1.53125,0.390625 -2,1.125 v -0.9375 h -0.9375 z M 3.40625,-5.53125 c 1.109375,0 1.828125,0.96875 1.828125,2.46875 0,1.4375 -0.734375,2.40625 -1.828125,2.40625 -1.0625,0 -1.75,-0.96875 -1.75,-2.4375 0,-1.484375 0.6875,-2.4375 1.75,-2.4375 z m 0,0"
           id="path16968" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-8">
        <path
           style="stroke:none"
           d="m 6.15625,-2.8125 c 0,-0.953125 -0.078125,-1.53125 -0.25,-2 C 5.5,-5.84375 4.53125,-6.46875 3.359375,-6.46875 c -1.75,0 -2.875,1.328125 -2.875,3.40625 0,2.078125 1.078125,3.34375 2.859375,3.34375 1.4375,0 2.421875,-0.828125 2.6875,-2.1875 H 5.015625 C 4.734375,-1.078125 4.171875,-0.640625 3.375,-0.640625 2.734375,-0.640625 2.203125,-0.9375 1.859375,-1.46875 1.625,-1.828125 1.53125,-2.1875 1.53125,-2.8125 Z M 1.546875,-3.625 C 1.625,-4.78125 2.34375,-5.546875 3.34375,-5.546875 4.375,-5.546875 5.078125,-4.75 5.078125,-3.625 Z m 0,0"
           id="path16971" />
      </symbol>
    </g>
    <g
       id="g46644">
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-0-3">
        <path
           style="stroke:none"
           d=""
           id="path46503" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-1-6">
        <path
           style="stroke:none"
           d="M 5.6875,-2.625 6.59375,0 h 1.25 L 4.765625,-8.75 h -1.4375 L 0.203125,0 h 1.1875 L 2.3125,-2.625 Z M 5.375,-3.5625 H 2.59375 l 1.4375,-3.984375 z m 0,0"
           id="path46506" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-2-7">
        <path
           style="stroke:none"
           d="M 1.828125,-8.75 H 0.8125 V 0 h 1.015625 z m 0,0"
           id="path46509" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-3-5">
        <path
           style="stroke:none"
           d=""
           id="path46512" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-4-3">
        <path
           style="stroke:none"
           d="m 5.25,-4.53125 c 0,-1.234375 -0.828125,-1.9375 -2.28125,-1.9375 -1.453125,0 -2.40625,0.75 -2.40625,1.921875 0,0.984375 0.5,1.453125 2,1.8125 l 0.921875,0.21875 c 0.703125,0.171875 0.984375,0.421875 0.984375,0.875 0,0.59375 -0.59375,1 -1.46875,1 -0.546875,0 -1,-0.15625 -1.25,-0.421875 C 1.59375,-1.25 1.53125,-1.421875 1.46875,-1.875 h -1.0625 c 0.046875,1.453125 0.859375,2.15625 2.515625,2.15625 1.578125,0 2.59375,-0.78125 2.59375,-2 0,-0.9375 -0.53125,-1.453125 -1.78125,-1.75 l -0.96875,-0.234375 c -0.8125,-0.1875 -1.15625,-0.453125 -1.15625,-0.890625 0,-0.59375 0.515625,-0.953125 1.328125,-0.953125 0.8125,0 1.234375,0.34375 1.265625,1.015625 z m 0,0"
           id="path46515" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-5-5">
        <path
           style="stroke:none"
           d="M 6.421875,-0.59375 C 6.3125,-0.5625 6.265625,-0.5625 6.203125,-0.5625 c -0.34375,0 -0.546875,-0.1875 -0.546875,-0.5 V -4.75 c 0,-1.125 -0.8125,-1.71875 -2.359375,-1.71875 -0.921875,0 -1.65625,0.265625 -2.078125,0.734375 -0.296875,0.328125 -0.421875,0.6875 -0.4375,1.3125 h 1 c 0.09375,-0.78125 0.546875,-1.125 1.484375,-1.125 0.90625,0 1.40625,0.34375 1.40625,0.9375 V -4.34375 C 4.65625,-3.90625 4.4375,-3.75 3.625,-3.640625 2.203125,-3.46875 1.984375,-3.421875 1.609375,-3.265625 0.875,-2.953125 0.5,-2.40625 0.5,-1.578125 0.5,-0.4375 1.296875,0.28125 2.5625,0.28125 3.359375,0.28125 4,0 4.703125,-0.640625 4.78125,0 5.09375,0.28125 5.734375,0.28125 c 0.21875,0 0.34375,-0.03125 0.6875,-0.109375 z m -1.75,-1.390625 c 0,0.34375 -0.09375,0.546875 -0.40625,0.828125 -0.40625,0.359375 -0.890625,0.5625 -1.484375,0.5625 -0.78125,0 -1.234375,-0.375 -1.234375,-1.015625 0,-0.65625 0.4375,-1 1.515625,-1.15625 1.0625,-0.140625 1.265625,-0.1875 1.609375,-0.34375 z m 0,0"
           id="path46518" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-6-6">
        <path
           style="stroke:none"
           d="M 0.84375,-6.28125 V 0 h 1 v -3.953125 c 0,-0.90625 0.671875,-1.640625 1.484375,-1.640625 0.734375,0 1.15625,0.453125 1.15625,1.265625 V 0 H 5.5 v -3.953125 c 0,-0.90625 0.65625,-1.640625 1.46875,-1.640625 0.734375,0 1.171875,0.46875 1.171875,1.265625 V 0 h 1 v -4.71875 c 0,-1.125 -0.640625,-1.75 -1.828125,-1.75 -0.828125,0 -1.34375,0.25 -1.921875,0.953125 -0.375,-0.671875 -0.875,-0.953125 -1.6875,-0.953125 -0.84375,0 -1.40625,0.3125 -1.9375,1.0625 v -0.875 z m 0,0"
           id="path46521" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-7-2">
        <path
           style="stroke:none"
           d="M 0.640625,2.609375 H 1.65625 V -0.65625 c 0.53125,0.640625 1.109375,0.9375 1.9375,0.9375 1.625,0 2.6875,-1.3125 2.6875,-3.3125 0,-2.109375 -1.03125,-3.4375 -2.703125,-3.4375 -0.859375,0 -1.53125,0.390625 -2,1.125 v -0.9375 h -0.9375 z M 3.40625,-5.53125 c 1.109375,0 1.828125,0.96875 1.828125,2.46875 0,1.4375 -0.734375,2.40625 -1.828125,2.40625 -1.0625,0 -1.75,-0.96875 -1.75,-2.4375 0,-1.484375 0.6875,-2.4375 1.75,-2.4375 z m 0,0"
           id="path46524" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-8-9">
        <path
           style="stroke:none"
           d="m 6.15625,-2.8125 c 0,-0.953125 -0.078125,-1.53125 -0.25,-2 C 5.5,-5.84375 4.53125,-6.46875 3.359375,-6.46875 c -1.75,0 -2.875,1.328125 -2.875,3.40625 0,2.078125 1.078125,3.34375 2.859375,3.34375 1.4375,0 2.421875,-0.828125 2.6875,-2.1875 H 5.015625 C 4.734375,-1.078125 4.171875,-0.640625 3.375,-0.640625 2.734375,-0.640625 2.203125,-0.9375 1.859375,-1.46875 1.625,-1.828125 1.53125,-2.1875 1.53125,-2.8125 Z M 1.546875,-3.625 C 1.625,-4.78125 2.34375,-5.546875 3.34375,-5.546875 4.375,-5.546875 5.078125,-4.75 5.078125,-3.625 Z m 0,0"
           id="path46527" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-9">
        <path
           style="stroke:none"
           d="m 0.953125,0 h 3.9375 C 5.71875,0 6.34375,-0.234375 6.796875,-0.734375 7.234375,-1.1875 7.46875,-1.8125 7.46875,-2.5 7.46875,-3.546875 7,-4.1875 5.875,-4.625 c 0.8125,-0.359375 1.21875,-1 1.21875,-1.90625 0,-0.640625 -0.234375,-1.203125 -0.703125,-1.609375 C 5.921875,-8.5625 5.34375,-8.75 4.5,-8.75 H 0.953125 Z M 2.0625,-4.984375 v -2.78125 h 2.15625 c 0.625,0 0.984375,0.078125 1.28125,0.3125 0.3125,0.234375 0.46875,0.59375 0.46875,1.078125 0,0.484375 -0.15625,0.84375 -0.46875,1.078125 -0.296875,0.234375 -0.65625,0.3125 -1.28125,0.3125 z m 0,4 V -4 h 2.71875 c 0.984375,0 1.578125,0.5625 1.578125,1.515625 0,0.9375 -0.59375,1.5 -1.578125,1.5 z m 0,0"
           id="path46530" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-10">
        <path
           style="stroke:none"
           d="M 7.9375,-6.03125 C 7.59375,-7.953125 6.484375,-8.890625 4.578125,-8.890625 c -1.1875,0 -2.125,0.375 -2.78125,1.09375 -0.78125,0.859375 -1.21875,2.109375 -1.21875,3.53125 0,1.4375 0.4375,2.671875 1.265625,3.515625 0.671875,0.703125 1.546875,1.03125 2.6875,1.03125 2.125,0 3.328125,-1.15625 3.59375,-3.46875 H 6.96875 C 6.875,-2.59375 6.75,-2.1875 6.578125,-1.84375 6.21875,-1.109375 5.46875,-0.703125 4.53125,-0.703125 c -1.734375,0 -2.84375,-1.390625 -2.84375,-3.578125 0,-2.25 1.046875,-3.625 2.75,-3.625 0.703125,0 1.375,0.203125 1.734375,0.546875 0.3125,0.296875 0.5,0.65625 0.625,1.328125 z m 0,0"
           id="path46533" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-11">
        <path
           style="stroke:none"
           d="m 2.078125,-8.75 h -1.125 V 0 h 5.4375 v -0.984375 h -4.3125 z m 0,0"
           id="path46536" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-12">
        <path
           style="stroke:none"
           d="M 6.078125,-1.046875 H 1.59375 c 0.109375,-0.71875 0.5,-1.171875 1.53125,-1.8125 L 4.328125,-3.53125 C 5.515625,-4.1875 6.125,-5.078125 6.125,-6.140625 6.125,-6.859375 5.84375,-7.53125 5.34375,-8 c -0.5,-0.453125 -1.125,-0.671875 -1.9375,-0.671875 -1.078125,0 -1.875,0.375 -2.34375,1.125 -0.3125,0.453125 -0.4375,1 -0.46875,1.875 h 1.0625 c 0.03125,-0.59375 0.109375,-0.9375 0.25,-1.234375 C 2.1875,-7.421875 2.734375,-7.75 3.375,-7.75 c 0.953125,0 1.671875,0.6875 1.671875,1.625 0,0.703125 -0.390625,1.296875 -1.140625,1.734375 L 2.796875,-3.75 C 1.015625,-2.71875 0.5,-1.90625 0.40625,-0.015625 h 5.671875 z m 0,0"
           id="path46539" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-13">
        <path
           style="stroke:none"
           d="m 6.9375,1.515625 h -7.203125 v 0.59375 H 6.9375 Z m 0,0"
           id="path46542" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-14">
        <path
           style="stroke:none"
           d="m 5.609375,0 2.46875,-7.328125 V 0 H 9.125 V -8.75 H 7.578125 L 5.046875,-1.125 2.453125,-8.75 H 0.90625 V 0 H 1.953125 V -7.328125 L 4.4375,0 Z m 0,0"
           id="path46545" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-15">
        <path
           style="stroke:none"
           d="M 4.640625,-3.4375 7.9375,-8.75 H 6.59375 L 4.109375,-4.484375 1.53125,-8.75 h -1.375 l 3.375,5.3125 V 0 h 1.109375 z m 0,0"
           id="path46548" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-16">
        <path
           style="stroke:none"
           d="m 2.234375,-3.765625 h 2.875 c 1,0 1.4375,0.484375 1.4375,1.5625 v 0.78125 c 0,0.53125 0.09375,1.0625 0.25,1.421875 h 1.34375 V -0.28125 C 7.734375,-0.5625 7.640625,-0.875 7.625,-2.046875 7.609375,-3.484375 7.375,-3.90625 6.4375,-4.3125 c 0.984375,-0.5 1.375,-1.09375 1.375,-2.09375 C 7.8125,-7.921875 6.875,-8.75 5.140625,-8.75 H 1.109375 V 0 h 1.125 z m 0,-0.984375 V -7.765625 H 4.9375 c 0.625,0 0.984375,0.09375 1.25,0.34375 0.296875,0.25 0.453125,0.640625 0.453125,1.15625 C 6.640625,-5.21875 6.125,-4.75 4.9375,-4.75 Z m 0,0"
           id="path46551" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-17">
        <path
           style="stroke:none"
           d="M 2.203125,-3.984375 H 6.375 V -4.96875 H 2.203125 v -2.796875 h 4.75 V -8.75 h -5.875 V 0 h 1.125 z m 0,0"
           id="path46554" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-18">
        <path
           style="stroke:none"
           d="m 1.0625,0 h 3.375 C 6.640625,0 8,-1.65625 8,-4.375 8,-7.09375 6.65625,-8.75 4.4375,-8.75 h -3.375 z m 1.125,-0.984375 v -6.78125 H 4.25 c 1.71875,0 2.640625,1.171875 2.640625,3.390625 0,2.234375 -0.921875,3.390625 -2.640625,3.390625 z m 0,0"
           id="path46557" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-19">
        <path
           style="stroke:none"
           d="m 6.625,-8.75 v 6.140625 c 0,1.1875 -0.859375,1.90625 -2.25,1.90625 -0.65625,0 -1.1875,-0.15625 -1.609375,-0.453125 C 2.34375,-1.5 2.140625,-1.9375 2.140625,-2.609375 V -8.75 h -1.125 v 6.140625 c 0,1.78125 1.28125,2.890625 3.359375,2.890625 2.046875,0 3.359375,-1.140625 3.359375,-2.890625 V -8.75 Z m 0,0"
           id="path46560" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-20">
        <path
           style="stroke:none"
           d="M 4.6875,-4.484375 7.640625,-8.75 H 6.3125 l -2.25,3.4375 -2.25,-3.4375 H 0.453125 L 3.359375,-4.484375 0.265625,0 H 1.625 L 4.015625,-3.640625 6.40625,0 h 1.375 z m 0,0"
           id="path46563" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-21">
        <path
           style="stroke:none"
           d="M 3.921875,-2.09375 V 0 h 1.0625 v -2.09375 h 1.25 v -0.953125 h -1.25 v -5.625 H 4.203125 L 0.34375,-3.21875 v 1.125 z m 0,-0.953125 H 1.265625 L 3.921875,-6.875 Z m 0,0"
           id="path46566" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-22">
        <path
           style="stroke:none"
           d="m 2.203125,-3.984375 h 4.75 V -4.96875 h -4.75 v -2.796875 h 4.9375 V -8.75 h -6.0625 V 0 h 6.28125 v -0.984375 h -5.15625 z m 0,0"
           id="path46569" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-23">
        <path
           style="stroke:none"
           d="M 4.25,-7.765625 H 7.109375 V -8.75 H 0.25 v 0.984375 H 3.125 V 0 H 4.25 Z m 0,0"
           id="path46572" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-24">
        <path
           style="stroke:none"
           d="m 4.703125,0 3.03125,-8.75 h -1.1875 L 4.125,-1.34375 1.5625,-8.75 H 0.359375 L 3.5,0 Z m 0,0"
           id="path46575" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-25">
        <path
           style="stroke:none"
           d="m 5.96875,-6.421875 c -0.203125,-1.421875 -1.109375,-2.25 -2.40625,-2.25 -0.9375,0 -1.78125,0.453125 -2.28125,1.234375 -0.53125,0.84375 -0.765625,1.90625 -0.765625,3.484375 0,1.453125 0.203125,2.375 0.71875,3.15625 C 1.6875,-0.09375 2.4375,0.28125 3.375,0.28125 c 1.609375,0 2.78125,-1.21875 2.78125,-2.90625 0,-1.59375 -1.078125,-2.734375 -2.609375,-2.734375 -0.828125,0 -1.5,0.3125 -1.953125,0.953125 0.015625,-2.140625 0.6875,-3.328125 1.890625,-3.328125 0.75,0 1.265625,0.46875 1.4375,1.3125 z m -2.546875,2 c 1.015625,0 1.65625,0.71875 1.65625,1.875 0,1.09375 -0.71875,1.890625 -1.6875,1.890625 -0.984375,0 -1.734375,-0.828125 -1.734375,-1.9375 0,-1.078125 0.71875,-1.828125 1.765625,-1.828125 z m 0,0"
           id="path46578" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-26">
        <path
           style="stroke:none"
           d="m 2.296875,-1.25 h -1.25 V 0 h 1.25 z m 0,0"
           id="path46581" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-27">
        <path
           style="stroke:none"
           d="M 7.75,-8.75 H 6.703125 v 7.15625 L 2.125,-8.75 H 0.90625 V 0 h 1.0625 V -7.09375 L 6.484375,0 H 7.75 Z m 0,0"
           id="path46584" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-28">
        <path
           style="stroke:none"
           d="M 3.109375,-6.1875 V 0 H 4.15625 v -8.671875 h -0.6875 c -0.375,1.328125 -0.609375,1.515625 -2.25,1.71875 V -6.1875 Z m 0,0"
           id="path46587" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-29">
        <path
           style="stroke:none"
           d="M 6.609375,-3.984375 V 0 h 1.125 v -8.75 h -1.125 v 3.78125 h -4.5 V -8.75 H 1 V 0 h 1.109375 v -3.984375 z m 0,0"
           id="path46590" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-30">
        <path
           style="stroke:none"
           d="M 4.65625,-6.28125 2.921875,-1.390625 1.3125,-6.28125 H 0.234375 l 2.125,6.3125 -0.375,0.984375 C 1.8125,1.46875 1.59375,1.625 1.171875,1.625 c -0.15625,0 -0.3125,-0.015625 -0.53125,-0.0625 V 2.453125 C 0.859375,2.5625 1.0625,2.609375 1.3125,2.609375 c 0.328125,0 0.671875,-0.09375 0.9375,-0.296875 0.3125,-0.21875 0.5,-0.484375 0.6875,-1 l 2.796875,-7.59375 z m 0,0"
           id="path46593" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-31">
        <path
           style="stroke:none"
           d="M 0.828125,-6.28125 V 0 H 1.84375 v -3.265625 c 0,-1.515625 0.625,-2.1875 2.015625,-2.140625 V -6.4375 C 3.6875,-6.453125 3.59375,-6.46875 3.46875,-6.46875 2.8125,-6.46875 2.328125,-6.078125 1.75,-5.140625 V -6.28125 Z m 0,0"
           id="path46596" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-32">
        <path
           style="stroke:none"
           d="m 5.9375,-8.75 h -1 V -5.5 C 4.53125,-6.125 3.859375,-6.46875 3.015625,-6.46875 c -1.640625,0 -2.703125,1.3125 -2.703125,3.3125 0,2.125 1.03125,3.4375 2.734375,3.4375 0.859375,0 1.46875,-0.328125 2,-1.109375 V 0 H 5.9375 Z m -2.75,3.21875 c 1.078125,0 1.75,0.953125 1.75,2.453125 0,1.453125 -0.6875,2.421875 -1.75,2.421875 -1.09375,0 -1.828125,-0.96875 -1.828125,-2.4375 0,-1.46875 0.734375,-2.4375 1.828125,-2.4375 z m 0,0"
           id="path46599" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-33">
        <path
           style="stroke:none"
           d="m 1.796875,-6.28125 h -1 V 0 h 1 z m 0,-2.46875 h -1 v 1.265625 h 1 z m 0,0"
           id="path46602" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-34">
        <path
           style="stroke:none"
           d="m 3.265625,-6.46875 c -1.78125,0 -2.828125,1.265625 -2.828125,3.375 0,2.125 1.046875,3.375 2.84375,3.375 1.765625,0 2.84375,-1.265625 2.84375,-3.328125 0,-2.1875 -1.03125,-3.421875 -2.859375,-3.421875 z m 0.015625,0.921875 c 1.125,0 1.796875,0.921875 1.796875,2.484375 0,1.484375 -0.703125,2.421875 -1.796875,2.421875 -1.125,0 -1.8125,-0.9375 -1.8125,-2.453125 0,-1.53125 0.6875,-2.453125 1.8125,-2.453125 z m 0,0"
           id="path46605" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-35">
        <path
           style="stroke:none"
           d="m 2.203125,-3.703125 h 2.75 c 0.6875,0 1.234375,-0.203125 1.6875,-0.625 C 7.171875,-4.8125 7.40625,-5.375 7.40625,-6.1875 7.40625,-7.828125 6.4375,-8.75 4.703125,-8.75 H 1.09375 V 0 h 1.109375 z m 0,-0.984375 V -7.765625 H 4.53125 c 1.078125,0 1.703125,0.578125 1.703125,1.53125 0,0.96875 -0.625,1.546875 -1.703125,1.546875 z m 0,0"
           id="path46608" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-36">
        <path
           style="stroke:none"
           d="m 2.328125,-8.75 h -1.125 V 0 h 1.125 z m 0,0"
           id="path46611" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-37">
        <path
           style="stroke:none"
           d="M 2.0625,-3.0625 3.484375,-4.484375 6.578125,0 h 1.3125 l -3.59375,-5.1875 3.5625,-3.5625 h -1.4375 L 2.0625,-4.3125 V -8.75 H 0.953125 V 0 H 2.0625 Z m 0,0"
           id="path46614" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-38">
        <path
           style="stroke:none"
           d="M 6.96875,-8.75 H 0.671875 v 0.984375 H 5.59375 l -5.25,6.78125 V 0 H 7 V -0.984375 H 1.734375 l 5.234375,-6.75 z m 0,0"
           id="path46617" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-39">
        <path
           style="stroke:none"
           d="M 0.84375,-6.28125 V 0 h 1 v -3.46875 c 0,-1.28125 0.671875,-2.125 1.703125,-2.125 0.796875,0 1.296875,0.484375 1.296875,1.234375 V 0 h 1 v -4.75 c 0,-1.046875 -0.78125,-1.71875 -1.984375,-1.71875 -0.9375,0 -1.546875,0.359375 -2.09375,1.234375 V -6.28125 Z m 0,0"
           id="path46620" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-40">
        <path
           style="stroke:none"
           d="M 5.71875,-8.515625 H 1.3125 L 0.6875,-3.875 h 0.96875 c 0.484375,-0.59375 0.90625,-0.796875 1.578125,-0.796875 1.140625,0 1.84375,0.78125 1.84375,2.046875 0,1.21875 -0.703125,1.96875 -1.859375,1.96875 -0.921875,0 -1.484375,-0.46875 -1.75,-1.4375 H 0.421875 C 0.5625,-1.390625 0.6875,-1.0625 0.9375,-0.75 c 0.484375,0.65625 1.34375,1.03125 2.296875,1.03125 1.71875,0 2.921875,-1.25 2.921875,-3.046875 0,-1.6875 -1.109375,-2.84375 -2.75,-2.84375 -0.59375,0 -1.078125,0.15625 -1.5625,0.515625 l 0.328125,-2.375 H 5.71875 Z m 0,0"
           id="path46623" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-41">
        <path
           style="stroke:none"
           d="M 0.640625,-1.984375 C 0.84375,-0.5625 1.75,0.28125 3.046875,0.28125 4,0.28125 4.84375,-0.1875 5.34375,-0.953125 5.875,-1.8125 6.109375,-2.875 6.109375,-4.4375 c 0,-1.46875 -0.21875,-2.390625 -0.71875,-3.15625 -0.46875,-0.703125 -1.21875,-1.078125 -2.15625,-1.078125 -1.609375,0 -2.78125,1.203125 -2.78125,2.890625 0,1.59375 1.078125,2.71875 2.625,2.71875 0.796875,0 1.390625,-0.28125 1.9375,-0.953125 C 5,-1.84375 4.328125,-0.65625 3.125,-0.65625 c -0.75,0 -1.265625,-0.484375 -1.4375,-1.328125 z M 3.234375,-7.75 c 0.984375,0 1.71875,0.828125 1.71875,1.9375 C 4.953125,-4.734375 4.234375,-4 3.1875,-4 2.171875,-4 1.53125,-4.71875 1.53125,-5.875 1.53125,-6.953125 2.25,-7.75 3.234375,-7.75 Z m 0,0"
           id="path46626" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-42">
        <path
           style="stroke:none"
           d="m 3.046875,-6.28125 h -1.03125 v -1.734375 h -1 v 1.734375 h -0.84375 v 0.8125 h 0.84375 v 4.75 c 0,0.640625 0.4375,1 1.21875,1 C 2.5,0.28125 2.71875,0.25 3.046875,0.1875 V -0.640625 C 2.90625,-0.609375 2.765625,-0.59375 2.5625,-0.59375 c -0.421875,0 -0.546875,-0.125 -0.546875,-0.5625 v -4.3125 h 1.03125 z m 0,0"
           id="path46629" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-43">
        <path
           style="stroke:none"
           d="m 4.6875,-4.578125 c 0.890625,-0.53125 1.171875,-0.96875 1.171875,-1.78125 0,-1.375 -1.046875,-2.3125 -2.5625,-2.3125 -1.5,0 -2.546875,0.9375 -2.546875,2.296875 0,0.828125 0.265625,1.25 1.140625,1.796875 -0.96875,0.5 -1.453125,1.203125 -1.453125,2.171875 0,1.578125 1.171875,2.6875 2.859375,2.6875 1.6875,0 2.859375,-1.109375 2.859375,-2.6875 0,-0.96875 -0.484375,-1.671875 -1.46875,-2.171875 z m -1.390625,-3.15625 c 0.90625,0 1.484375,0.53125 1.484375,1.390625 0,0.828125 -0.59375,1.359375 -1.484375,1.359375 -0.890625,0 -1.46875,-0.53125 -1.46875,-1.375 0,-0.84375 0.578125,-1.375 1.46875,-1.375 z m 0,3.640625 c 1.0625,0 1.78125,0.703125 1.78125,1.703125 0,1.046875 -0.703125,1.734375 -1.796875,1.734375 -1.03125,0 -1.75,-0.71875 -1.75,-1.71875 0,-1.03125 0.703125,-1.71875 1.765625,-1.71875 z m 0,0"
           id="path46632" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-44">
        <path
           style="stroke:none"
           d="m 3.296875,-8.671875 c -0.78125,0 -1.515625,0.359375 -1.953125,0.9375 -0.546875,0.78125 -0.828125,1.921875 -0.828125,3.53125 0,2.9375 0.953125,4.484375 2.78125,4.484375 1.796875,0 2.78125,-1.546875 2.78125,-4.40625 0,-1.6875 -0.265625,-2.8125 -0.828125,-3.609375 -0.4375,-0.59375 -1.140625,-0.9375 -1.953125,-0.9375 z m 0,0.9375 C 4.4375,-7.734375 5,-6.578125 5,-4.21875 c 0,2.46875 -0.546875,3.625 -1.71875,3.625 -1.125,0 -1.6875,-1.203125 -1.6875,-3.59375 0,-2.390625 0.5625,-3.546875 1.703125,-3.546875 z m 0,0"
           id="path46635" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-45">
        <path
           style="stroke:none"
           d="M 0.84375,-8.75 V 0 h 1 v -3.46875 c 0,-1.28125 0.671875,-2.125 1.703125,-2.125 0.328125,0 0.640625,0.09375 0.875,0.28125 0.296875,0.21875 0.421875,0.515625 0.421875,0.953125 V 0 h 0.984375 v -4.75 c 0,-1.0625 -0.75,-1.71875 -1.96875,-1.71875 -0.890625,0 -1.4375,0.28125 -2.015625,1.046875 V -8.75 Z m 0,0"
           id="path46638" />
      </symbol>
      <symbol
         style="overflow:visible"
         overflow="visible"
         id="glyph0-46">
        <path
           style="stroke:none"
           d="m 2.65625,-4 h 0.578125 c 1.140625,0 1.75,0.546875 1.75,1.59375 0,1.09375 -0.65625,1.75 -1.75,1.75 -1.15625,0 -1.71875,-0.59375 -1.796875,-1.859375 H 0.390625 c 0.046875,0.6875 0.15625,1.140625 0.359375,1.53125 0.453125,0.84375 1.28125,1.265625 2.4375,1.265625 1.75,0 2.890625,-1.0625 2.890625,-2.703125 C 6.078125,-3.53125 5.65625,-4.125 4.625,-4.484375 5.421875,-4.8125 5.8125,-5.40625 5.8125,-6.28125 c 0,-1.5 -0.96875,-2.390625 -2.578125,-2.390625 -1.71875,0 -2.640625,0.953125 -2.671875,2.796875 H 1.625 c 0,-0.53125 0.0625,-0.828125 0.1875,-1.09375 0.234375,-0.5 0.765625,-0.78125 1.421875,-0.78125 0.9375,0 1.5,0.5625 1.5,1.5 0,0.609375 -0.203125,0.984375 -0.671875,1.1875 -0.296875,0.125 -0.671875,0.171875 -1.40625,0.171875 z m 0,0"
           id="path46641" />
      </symbol>
    </g>
    <g
       id="g450">
      <symbol
         id="glyph0-0-36"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path405"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-1-7"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path408"
           d="M 8.1875,-3.78125 9.484375,0 H 11.28125 L 6.859375,-12.59375 H 4.78125 L 0.296875,0 H 2 L 3.328125,-3.78125 Z M 7.734375,-5.125 h -4 l 2.078125,-5.75 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-2-5"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path411"
           d="M 9.546875,-12.59375 V -3.75 c 0,1.6875 -1.234375,2.734375 -3.25,2.734375 -0.9375,0 -1.703125,-0.234375 -2.3125,-0.65625 C 3.375,-2.15625 3.078125,-2.796875 3.078125,-3.75 v -8.84375 H 1.46875 V -3.75 c 0,2.5625 1.828125,4.140625 4.828125,4.140625 2.953125,0 4.84375,-1.625 4.84375,-4.140625 v -8.84375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-3-3"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path414"
           d="M 3.296875,-1.796875 H 1.5 V 0 h 1.796875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-4-5"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path417"
           d="M 4.46875,-8.90625 V 0 H 6 V -12.5 H 5 c -0.546875,1.921875 -0.890625,2.1875 -3.234375,2.5 v 1.09375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-5-6"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path420"
           d="M 8.75,-1.5 H 2.296875 C 2.453125,-2.546875 3,-3.203125 4.515625,-4.109375 l 1.71875,-0.96875 c 1.71875,-0.953125 2.59375,-2.234375 2.59375,-3.765625 0,-1.046875 -0.40625,-2.015625 -1.140625,-2.6875 C 6.96875,-12.1875 6.0625,-12.5 4.90625,-12.5 c -1.546875,0 -2.71875,0.5625 -3.390625,1.625 -0.421875,0.65625 -0.609375,1.4375 -0.65625,2.703125 h 1.53125 C 2.4375,-9.015625 2.546875,-9.515625 2.75,-9.9375 c 0.390625,-0.765625 1.1875,-1.21875 2.109375,-1.21875 1.375,0 2.421875,1 2.421875,2.34375 0,1 -0.578125,1.859375 -1.671875,2.484375 l -1.578125,0.9375 c -2.5625,1.46875 -3.3125,2.640625 -3.4375,5.375 H 8.75 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-6-2"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path423"
           d="m 3.8125,-5.75 h 0.84375 c 1.65625,0 2.53125,0.765625 2.53125,2.28125 0,1.5625 -0.953125,2.515625 -2.515625,2.515625 -1.6875,0 -2.5,-0.84375 -2.59375,-2.671875 h -1.53125 c 0.078125,1 0.25,1.65625 0.546875,2.203125 0.640625,1.21875 1.828125,1.8125 3.5,1.8125 C 7.125,0.390625 8.75,-1.125 8.75,-3.484375 8.75,-5.078125 8.140625,-5.9375 6.671875,-6.46875 7.8125,-6.9375 8.375,-7.796875 8.375,-9.0625 8.375,-11.203125 6.984375,-12.5 4.65625,-12.5 c -2.484375,0 -3.796875,1.390625 -3.84375,4.03125 h 1.515625 c 0.015625,-0.765625 0.09375,-1.1875 0.28125,-1.578125 0.34375,-0.703125 1.109375,-1.109375 2.0625,-1.109375 1.34375,0 2.15625,0.8125 2.15625,2.15625 0,0.875 -0.3125,1.40625 -0.984375,1.703125 C 5.421875,-7.125 4.875,-7.046875 3.8125,-7.03125 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-0"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path426"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-1"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path429"
           d="m 1.1875,0 h 4.71875 c 1.203125,0 2.015625,-0.234375 2.65625,-0.765625 0.625,-0.53125 1.03125,-1.40625 1.03125,-2.265625 0,-1.03125 -0.546875,-1.859375 -1.75,-2.546875 1.046875,-0.65625 1.453125,-1.265625 1.453125,-2.15625 0,-0.734375 -0.359375,-1.484375 -0.953125,-2 C 7.71875,-10.265625 6.984375,-10.5 5.859375,-10.5 H 1.1875 Z M 3.34375,-8.703125 H 5.6875 c 1.015625,0 1.53125,0.40625 1.53125,1.1875 0,0.78125 -0.515625,1.1875 -1.53125,1.1875 H 3.34375 Z m 0,4.171875 h 2.578125 c 1.046875,0 1.59375,0.46875 1.59375,1.375 0,0.890625 -0.546875,1.359375 -1.59375,1.359375 H 3.34375 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-2"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path432"
           d="M 9.828125,-6.9375 C 9.75,-7.84375 9.5625,-8.421875 9.125,-9.015625 c -0.8125,-1.0625 -2.109375,-1.65625 -3.671875,-1.65625 -2.96875,0 -4.8125,2.109375 -4.8125,5.515625 0,3.390625 1.828125,5.484375 4.75,5.484375 2.625,0 4.34375,-1.515625 4.484375,-3.921875 H 7.765625 C 7.625,-2.25 6.78125,-1.484375 5.453125,-1.484375 c -1.671875,0 -2.65625,-1.359375 -2.65625,-3.640625 0,-2.328125 1.015625,-3.703125 2.71875,-3.703125 1.25,0 1.96875,0.609375 2.25,1.890625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-3"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path435"
           d="M 3.3125,-10.5 H 1.15625 V 0 h 7.1875 V -1.796875 H 3.3125 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-4"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path438"
           d="M 7.375,-1.796875 H 3.046875 C 3.3125,-2.34375 3.625,-2.65625 5.125,-3.734375 6.90625,-5.03125 7.421875,-5.796875 7.421875,-7.1875 c 0,-1.96875 -1.375,-3.25 -3.5,-3.25 -2.125,0 -3.359375,1.265625 -3.359375,3.421875 V -6.65625 H 2.5 V -6.984375 C 2.5,-8.125 3.046875,-8.78125 3.96875,-8.78125 c 0.890625,0 1.4375,0.609375 1.4375,1.640625 C 5.40625,-6 5.0625,-5.59375 2.78125,-3.96875 1.046875,-2.796875 0.515625,-1.90625 0.4375,0 H 7.375 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-5"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path441"
           d="M 3,-10.28125 0.03125,0.203125 H 1 L 3.96875,-10.28125 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-6"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path444"
           d="M 3.109375,-8.1875 5,0 H 7.15625 L 9.015625,-8.1875 V 0 h 2.15625 v -10.5 h -3.25 L 6.078125,-2.140625 4.171875,-10.5 H 0.953125 V 0 h 2.15625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-7"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path447"
           d="M 6.03125,-3.890625 9.359375,-10.5 H 6.9375 l -2,4.640625 L 2.796875,-10.5 H 0.390625 L 3.875,-3.890625 V 0 h 2.15625 z m 0,0"
           style="stroke:none" />
      </symbol>
    </g>
    <g
       id="g6718">
      <symbol
         id="glyph0-0-8"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6685"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-1-9"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6688"
           d="M 8.1875,-3.78125 9.484375,0 H 11.28125 L 6.859375,-12.59375 H 4.78125 L 0.296875,0 H 2 L 3.328125,-3.78125 Z M 7.734375,-5.125 h -4 l 2.078125,-5.75 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-2-73"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6691"
           d="M 9.546875,-12.59375 V -3.75 c 0,1.6875 -1.234375,2.734375 -3.25,2.734375 -0.9375,0 -1.703125,-0.234375 -2.3125,-0.65625 C 3.375,-2.15625 3.078125,-2.796875 3.078125,-3.75 v -8.84375 H 1.46875 V -3.75 c 0,2.5625 1.828125,4.140625 4.828125,4.140625 2.953125,0 4.84375,-1.625 4.84375,-4.140625 v -8.84375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-3-6"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6694"
           d="M 3.296875,-1.796875 H 1.5 V 0 h 1.796875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-4-1"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6697"
           d="m 4.75,-12.5 c -1.140625,0 -2.171875,0.53125 -2.8125,1.375 -0.796875,1.109375 -1.1875,2.765625 -1.1875,5.078125 0,4.21875 1.375,6.4375 4,6.4375 2.59375,0 4.015625,-2.21875 4.015625,-6.328125 C 8.765625,-8.359375 8.375,-9.984375 7.5625,-11.125 6.9375,-12 5.90625,-12.5 4.75,-12.5 Z m 0,1.359375 c 1.640625,0 2.453125,1.671875 2.453125,5.0625 0,3.5625 -0.796875,5.21875 -2.484375,5.21875 -1.609375,0 -2.421875,-1.734375 -2.421875,-5.171875 0,-3.4375 0.8125,-5.109375 2.453125,-5.109375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-5-2"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6700"
           d="M 8.75,-1.5 H 2.296875 C 2.453125,-2.546875 3,-3.203125 4.515625,-4.109375 l 1.71875,-0.96875 c 1.71875,-0.953125 2.59375,-2.234375 2.59375,-3.765625 0,-1.046875 -0.40625,-2.015625 -1.140625,-2.6875 C 6.96875,-12.1875 6.0625,-12.5 4.90625,-12.5 c -1.546875,0 -2.71875,0.5625 -3.390625,1.625 -0.421875,0.65625 -0.609375,1.4375 -0.65625,2.703125 h 1.53125 C 2.4375,-9.015625 2.546875,-9.515625 2.75,-9.9375 c 0.390625,-0.765625 1.1875,-1.21875 2.109375,-1.21875 1.375,0 2.421875,1 2.421875,2.34375 0,1 -0.578125,1.859375 -1.671875,2.484375 l -1.578125,0.9375 c -2.5625,1.46875 -3.3125,2.640625 -3.4375,5.375 H 8.75 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-6-9"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6703"
           d="M 4.46875,-8.90625 V 0 H 6 V -12.5 H 5 c -0.546875,1.921875 -0.890625,2.1875 -3.234375,2.5 v 1.09375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-0-3"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6706"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-1-1"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6709"
           d="M 3.25,-3.75 H 5.953125 C 7.875,-3.75 9.125,-5.109375 9.125,-7.25 9.125,-9.34375 7.921875,-10.5 5.734375,-10.5 H 1.09375 V 0 H 3.25 Z m 0,-1.796875 v -3.15625 h 2.015625 c 1.15625,0 1.6875,0.5 1.6875,1.578125 0,1.078125 -0.53125,1.578125 -1.6875,1.578125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-2-9"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6712"
           d="M 0.96875,-10.5 V 0 H 2.984375 V -4.671875 C 2.984375,-5.5625 3.625,-6.1875 4.53125,-6.1875 c 0.453125,0 0.78125,0.15625 1.015625,0.46875 C 5.734375,-5.453125 5.78125,-5.25 5.78125,-4.75 V 0 H 7.796875 V -5.21875 C 7.796875,-6.1875 7.53125,-6.875 7,-7.3125 6.5625,-7.6875 5.90625,-7.90625 5.265625,-7.90625 c -1,0 -1.71875,0.390625 -2.28125,1.25 V -10.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-3-4"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path6715"
           d="M 7.671875,-4.1875 H 5.0625 v -2.625 H 3.34375 v 2.625 h -2.625 v 1.703125 h 2.625 v 2.625 H 5.0625 v -2.625 h 2.609375 z m 0,0"
           style="stroke:none" />
      </symbol>
    </g>
    <g
       id="g13143">
      <symbol
         id="glyph0-0-5"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12930"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-1-0"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12933"
           d="M 8.1875,-3.78125 9.484375,0 H 11.28125 L 6.859375,-12.59375 H 4.78125 L 0.296875,0 H 2 L 3.328125,-3.78125 Z M 7.734375,-5.125 h -4 l 2.078125,-5.75 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-2-3"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12936"
           d="M 9.546875,-12.59375 V -3.75 c 0,1.6875 -1.234375,2.734375 -3.25,2.734375 -0.9375,0 -1.703125,-0.234375 -2.3125,-0.65625 C 3.375,-2.15625 3.078125,-2.796875 3.078125,-3.75 v -8.84375 H 1.46875 V -3.75 c 0,2.5625 1.828125,4.140625 4.828125,4.140625 2.953125,0 4.84375,-1.625 4.84375,-4.140625 v -8.84375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-3-61"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12939"
           d="M 3.296875,-1.796875 H 1.5 V 0 h 1.796875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-4-0"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12942"
           d="m 4.75,-12.5 c -1.140625,0 -2.171875,0.53125 -2.8125,1.375 -0.796875,1.109375 -1.1875,2.765625 -1.1875,5.078125 0,4.21875 1.375,6.4375 4,6.4375 2.59375,0 4.015625,-2.21875 4.015625,-6.328125 C 8.765625,-8.359375 8.375,-9.984375 7.5625,-11.125 6.9375,-12 5.90625,-12.5 4.75,-12.5 Z m 0,1.359375 c 1.640625,0 2.453125,1.671875 2.453125,5.0625 0,3.5625 -0.796875,5.21875 -2.484375,5.21875 -1.609375,0 -2.421875,-1.734375 -2.421875,-5.171875 0,-3.4375 0.8125,-5.109375 2.453125,-5.109375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-5-63"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12945"
           d="M 8.75,-1.5 H 2.296875 C 2.453125,-2.546875 3,-3.203125 4.515625,-4.109375 l 1.71875,-0.96875 c 1.71875,-0.953125 2.59375,-2.234375 2.59375,-3.765625 0,-1.046875 -0.40625,-2.015625 -1.140625,-2.6875 C 6.96875,-12.1875 6.0625,-12.5 4.90625,-12.5 c -1.546875,0 -2.71875,0.5625 -3.390625,1.625 -0.421875,0.65625 -0.609375,1.4375 -0.65625,2.703125 h 1.53125 C 2.4375,-9.015625 2.546875,-9.515625 2.75,-9.9375 c 0.390625,-0.765625 1.1875,-1.21875 2.109375,-1.21875 1.375,0 2.421875,1 2.421875,2.34375 0,1 -0.578125,1.859375 -1.671875,2.484375 l -1.578125,0.9375 c -2.5625,1.46875 -3.3125,2.640625 -3.4375,5.375 H 8.75 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph0-6-20"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12948"
           d="M 4.46875,-8.90625 V 0 H 6 V -12.5 H 5 c -0.546875,1.921875 -0.890625,2.1875 -3.234375,2.5 v 1.09375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-0-6"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12951"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-1-15"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12954"
           d="M 3.25,-3.75 H 5.953125 C 7.875,-3.75 9.125,-5.109375 9.125,-7.25 9.125,-9.34375 7.921875,-10.5 5.734375,-10.5 H 1.09375 V 0 H 3.25 Z m 0,-1.796875 v -3.15625 h 2.015625 c 1.15625,0 1.6875,0.5 1.6875,1.578125 0,1.078125 -0.53125,1.578125 -1.6875,1.578125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-2-5"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12957"
           d="M 0.96875,-10.5 V 0 H 2.984375 V -4.671875 C 2.984375,-5.5625 3.625,-6.1875 4.53125,-6.1875 c 0.453125,0 0.78125,0.15625 1.015625,0.46875 C 5.734375,-5.453125 5.78125,-5.25 5.78125,-4.75 V 0 H 7.796875 V -5.21875 C 7.796875,-6.1875 7.53125,-6.875 7,-7.3125 6.5625,-7.6875 5.90625,-7.90625 5.265625,-7.90625 c -1,0 -1.71875,0.390625 -2.28125,1.25 V -10.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph1-3-47"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12960"
           d="M 7.671875,-4.1875 H 5.0625 v -2.625 H 3.34375 v 2.625 h -2.625 v 1.703125 h 2.625 v 2.625 H 5.0625 v -2.625 h 2.609375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-0"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12963"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-1"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12966"
           d="m 2.65625,-4.453125 h 3.296875 c 0.8125,0 1.46875,-0.25 2.03125,-0.75 0.625,-0.578125 0.90625,-1.25 0.90625,-2.21875 0,-1.96875 -1.171875,-3.078125 -3.25,-3.078125 H 1.3125 V 0 h 1.34375 z m 0,-1.1875 v -3.6875 h 2.796875 c 1.28125,0 2.03125,0.703125 2.03125,1.84375 0,1.15625 -0.75,1.84375 -2.03125,1.84375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-2"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12969"
           d="M 1,-7.546875 V 0 H 2.203125 V -3.921875 C 2.21875,-5.734375 2.96875,-6.546875 4.625,-6.5 V -7.71875 C 4.421875,-7.75 4.3125,-7.765625 4.15625,-7.765625 c -0.765625,0 -1.359375,0.46875 -2.046875,1.578125 v -1.359375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-3"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12972"
           d="m 3.921875,-7.765625 c -2.140625,0 -3.40625,1.515625 -3.40625,4.046875 0,2.546875 1.265625,4.046875 3.421875,4.046875 2.125,0 3.40625,-1.515625 3.40625,-3.984375 0,-2.625 -1.234375,-4.109375 -3.421875,-4.109375 z M 3.9375,-6.65625 c 1.34375,0 2.15625,1.109375 2.15625,2.984375 0,1.78125 -0.828125,2.890625 -2.15625,2.890625 -1.34375,0 -2.171875,-1.109375 -2.171875,-2.9375 0,-1.828125 0.828125,-2.9375 2.171875,-2.9375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-4"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12975"
           d="m 4.203125,-3.90625 2.53125,-3.640625 H 5.390625 L 3.578125,-4.8125 1.75,-7.546875 H 0.390625 L 2.90625,-3.84375 0.25,0 H 1.609375 L 3.53125,-2.890625 5.421875,0 H 6.8125 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-5"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12978"
           d="M 2.15625,-7.546875 H 0.96875 V 0 h 1.1875 z m 0,-2.953125 H 0.953125 v 1.515625 H 2.15625 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-6"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12981"
           d="M 1.015625,-7.546875 V 0 H 2.21875 v -4.734375 c 0,-1.09375 0.796875,-1.984375 1.765625,-1.984375 0.90625,0 1.40625,0.546875 1.40625,1.515625 V 0 H 6.59375 v -4.734375 c 0,-1.09375 0.796875,-1.984375 1.78125,-1.984375 0.875,0 1.390625,0.5625 1.390625,1.515625 V 0 h 1.21875 v -5.65625 c 0,-1.359375 -0.78125,-2.109375 -2.203125,-2.109375 -1,0 -1.609375,0.296875 -2.3125,1.15625 -0.453125,-0.8125 -1.046875,-1.15625 -2.03125,-1.15625 -1.015625,0 -1.6875,0.375 -2.3125,1.28125 v -1.0625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-7"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12984"
           d="M 3.65625,-7.546875 H 2.421875 V -9.625 H 1.21875 v 2.078125 H 0.203125 V -6.5625 H 1.21875 v 5.703125 c 0,0.765625 0.53125,1.1875 1.453125,1.1875 C 3,0.328125 3.25,0.296875 3.65625,0.234375 V -0.78125 c -0.171875,0.046875 -0.328125,0.0625 -0.578125,0.0625 -0.515625,0 -0.65625,-0.140625 -0.65625,-0.671875 V -6.5625 H 3.65625 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-8"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12987"
           d="m 5.59375,-7.546875 -2.09375,5.875 -1.9375,-5.875 H 0.28125 L 2.84375,0.03125 2.375,1.21875 C 2.171875,1.75 1.921875,1.953125 1.40625,1.953125 1.203125,1.953125 1.03125,1.9375 0.78125,1.875 v 1.078125 c 0.234375,0.125 0.484375,0.1875 0.796875,0.1875 0.390625,0 0.8125,-0.125 1.125,-0.359375 C 3.078125,2.5 3.296875,2.1875 3.53125,1.578125 l 3.359375,-9.125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-9"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12990"
           d="m 3.078125,-1.5 h -1.5 V 0 h 1.5 z m 0,-6.046875 h -1.5 v 1.5 h 1.5 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-10"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12993"
           d=""
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-11"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12996"
           d="m 0.765625,-2.375 c 0.25,1.703125 1.34375,2.703125 2.890625,2.703125 1.140625,0 2.15625,-0.546875 2.75,-1.484375 0.640625,-1.015625 0.921875,-2.28125 0.921875,-4.171875 0,-1.765625 -0.25,-2.875 -0.859375,-3.796875 -0.5625,-0.84375 -1.453125,-1.296875 -2.578125,-1.296875 -1.953125,0 -3.34375,1.46875 -3.34375,3.484375 0,1.90625 1.296875,3.265625 3.140625,3.265625 0.96875,0 1.6875,-0.34375 2.328125,-1.140625 C 6,-2.21875 5.203125,-0.796875 3.75,-0.796875 2.859375,-0.796875 2.234375,-1.375 2.03125,-2.375 Z M 3.875,-9.3125 c 1.1875,0 2.078125,1 2.078125,2.34375 0,1.28125 -0.875,2.171875 -2.125,2.171875 -1.21875,0 -1.984375,-0.859375 -1.984375,-2.25 0,-1.3125 0.84375,-2.265625 2.03125,-2.265625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-12"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path12999"
           d="m 5.640625,-5.484375 c 1.0625,-0.65625 1.390625,-1.171875 1.390625,-2.15625 0,-1.640625 -1.25,-2.78125 -3.0625,-2.78125 -1.8125,0 -3.078125,1.140625 -3.078125,2.765625 0,1 0.328125,1.5 1.390625,2.171875 -1.171875,0.59375 -1.75,1.4375 -1.75,2.59375 0,1.890625 1.40625,3.21875 3.4375,3.21875 2.015625,0 3.421875,-1.328125 3.421875,-3.21875 0,-1.15625 -0.578125,-2 -1.75,-2.59375 z m -1.671875,-3.8125 c 1.078125,0 1.765625,0.65625 1.765625,1.6875 0,0.984375 -0.703125,1.625 -1.765625,1.625 -1.09375,0 -1.78125,-0.640625 -1.78125,-1.65625 0,-1 0.6875,-1.65625 1.78125,-1.65625 z m 0,4.390625 c 1.265625,0 2.125,0.828125 2.125,2.046875 0,1.25 -0.84375,2.0625 -2.15625,2.0625 -1.25,0 -2.109375,-0.84375 -2.109375,-2.0625 0,-1.234375 0.84375,-2.046875 2.140625,-2.046875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-13"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13002"
           d="m 2.859375,-9.875 c -1.34375,0 -2.4375,1.109375 -2.4375,2.46875 0,1.359375 1.09375,2.46875 2.453125,2.46875 1.34375,0 2.453125,-1.109375 2.453125,-2.4375 0,-1.390625 -1.078125,-2.5 -2.46875,-2.5 z m 0,1.015625 c 0.828125,0 1.484375,0.640625 1.484375,1.46875 0,0.796875 -0.671875,1.4375 -1.46875,1.4375 -0.796875,0 -1.46875,-0.640625 -1.46875,-1.453125 0,-0.8125 0.65625,-1.453125 1.453125,-1.453125 z m 5.90625,-1.359375 -5.6875,10.5 H 4.03125 l 5.6875,-10.5 z m 1.140625,5.578125 c -1.34375,0 -2.4375,1.09375 -2.4375,2.453125 0,1.359375 1.09375,2.46875 2.453125,2.46875 1.34375,0 2.453125,-1.109375 2.453125,-2.4375 0,-1.390625 -1.078125,-2.484375 -2.46875,-2.484375 z m 0,1.015625 c 0.828125,0 1.46875,0.640625 1.46875,1.46875 0,0.765625 -0.65625,1.421875 -1.453125,1.421875 -0.8125,0 -1.46875,-0.65625 -1.46875,-1.453125 0,-0.796875 0.65625,-1.4375 1.453125,-1.4375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-14"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13005"
           d="m 2.640625,-4.78125 h 5.71875 v -1.1875 h -5.71875 v -3.359375 h 5.9375 V -10.5 H 1.296875 V 0 h 7.53125 v -1.1875 h -6.1875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-15"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13008"
           d="m 6.78125,-5.015625 c -0.046875,-0.734375 -0.21875,-1.203125 -0.5,-1.625 -0.515625,-0.703125 -1.421875,-1.125 -2.484375,-1.125 -2.046875,0 -3.34375,1.609375 -3.34375,4.125 0,2.4375 1.296875,3.96875 3.328125,3.96875 1.8125,0 2.953125,-1.078125 3.09375,-2.921875 H 5.65625 c -0.203125,1.203125 -0.8125,1.8125 -1.84375,1.8125 -1.3125,0 -2.109375,-1.078125 -2.109375,-2.859375 0,-1.890625 0.78125,-3.015625 2.078125,-3.015625 1.015625,0 1.65625,0.59375 1.796875,1.640625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-16"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13011"
           d="M 2.1875,-10.5 H 0.984375 V 0 H 2.1875 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-17"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13014"
           d="M 6.9375,0 V -7.546875 H 5.75 v 4.28125 c 0,1.53125 -0.8125,2.546875 -2.0625,2.546875 -0.953125,0 -1.5625,-0.578125 -1.5625,-1.484375 v -5.34375 H 0.9375 v 5.8125 c 0,1.265625 0.9375,2.0625 2.40625,2.0625 1.109375,0 1.8125,-0.390625 2.515625,-1.375 V 0 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-18"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13017"
           d="m 6.3125,-5.453125 c -0.015625,-1.46875 -1,-2.3125 -2.734375,-2.3125 -1.765625,0 -2.90625,0.90625 -2.90625,2.3125 0,1.171875 0.609375,1.734375 2.390625,2.171875 l 1.125,0.265625 C 5.03125,-2.8125 5.359375,-2.5 5.359375,-1.96875 c 0,0.71875 -0.703125,1.1875 -1.765625,1.1875 -0.640625,0 -1.1875,-0.1875 -1.484375,-0.5 C 1.921875,-1.5 1.828125,-1.71875 1.75,-2.25 H 0.484375 C 0.546875,-0.5 1.53125,0.328125 3.5,0.328125 c 1.90625,0 3.109375,-0.9375 3.109375,-2.390625 0,-1.125 -0.625,-1.734375 -2.125,-2.09375 L 3.328125,-4.4375 C 2.34375,-4.671875 1.9375,-4.984375 1.9375,-5.515625 c 0,-0.703125 0.609375,-1.140625 1.59375,-1.140625 0.96875,0 1.484375,0.421875 1.515625,1.203125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-19"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13020"
           d="M 4.109375,0 7,-7.546875 H 5.640625 l -2.125,6.125 L 1.5,-7.546875 H 0.140625 L 2.796875,0 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-20"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13023"
           d="M 3.734375,-7.421875 V 0 H 5 V -10.421875 H 4.15625 C 3.71875,-8.8125 3.421875,-8.59375 1.46875,-8.34375 v 0.921875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-21"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13026"
           d="m 3.96875,-10.421875 c -0.953125,0 -1.828125,0.4375 -2.359375,1.140625 -0.65625,0.921875 -0.984375,2.3125 -0.984375,4.234375 0,3.515625 1.140625,5.375 3.34375,5.375 2.15625,0 3.328125,-1.859375 3.328125,-5.28125 0,-2.015625 -0.3125,-3.375 -0.984375,-4.328125 C 5.78125,-10 4.921875,-10.421875 3.96875,-10.421875 Z m 0,1.125 c 1.359375,0 2.03125,1.40625 2.03125,4.21875 0,2.96875 -0.65625,4.359375 -2.0625,4.359375 -1.34375,0 -2.015625,-1.4375 -2.015625,-4.3125 0,-2.859375 0.671875,-4.265625 2.046875,-4.265625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-22"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13029"
           d="M 9.53125,-7.25 C 9.125,-9.546875 7.796875,-10.671875 5.484375,-10.671875 c -1.40625,0 -2.546875,0.4375 -3.328125,1.3125 -0.953125,1.03125 -1.46875,2.53125 -1.46875,4.234375 0,1.71875 0.53125,3.203125 1.515625,4.234375 0.828125,0.828125 1.859375,1.21875 3.234375,1.21875 2.5625,0 4,-1.375 4.3125,-4.15625 H 8.375 C 8.25,-3.109375 8.109375,-2.625 7.890625,-2.203125 7.46875,-1.34375 6.5625,-0.84375 5.453125,-0.84375 3.359375,-0.84375 2.03125,-2.515625 2.03125,-5.140625 2.03125,-7.84375 3.28125,-9.5 5.328125,-9.5 6.1875,-9.5 6.96875,-9.25 7.40625,-8.828125 7.796875,-8.46875 8.015625,-8.03125 8.171875,-7.25 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-23"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13032"
           d="m 7.703125,-0.703125 c -0.125,0.03125 -0.1875,0.03125 -0.25,0.03125 -0.421875,0 -0.65625,-0.21875 -0.65625,-0.59375 v -4.4375 c 0,-1.34375 -0.984375,-2.0625 -2.828125,-2.0625 -1.109375,0 -2,0.3125 -2.515625,0.875 C 1.109375,-6.5 0.96875,-6.0625 0.9375,-5.3125 h 1.203125 c 0.109375,-0.921875 0.65625,-1.34375 1.78125,-1.34375 1.09375,0 1.6875,0.40625 1.6875,1.125 v 0.3125 C 5.59375,-4.703125 5.328125,-4.515625 4.34375,-4.375 2.65625,-4.15625 2.390625,-4.109375 1.9375,-3.921875 1.046875,-3.546875 0.609375,-2.875 0.609375,-1.90625 c 0,1.375 0.953125,2.234375 2.46875,2.234375 0.953125,0 1.71875,-0.328125 2.5625,-1.109375 0.09375,0.78125 0.46875,1.109375 1.25,1.109375 0.25,0 0.40625,-0.03125 0.8125,-0.125 z M 5.609375,-2.375 c 0,0.40625 -0.125,0.640625 -0.484375,0.984375 -0.484375,0.4375 -1.078125,0.671875 -1.78125,0.671875 -0.9375,0 -1.484375,-0.453125 -1.484375,-1.21875 0,-0.78125 0.515625,-1.1875 1.8125,-1.375 1.28125,-0.171875 1.53125,-0.234375 1.9375,-0.421875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-24"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13035"
           d="m 7.390625,-3.375 c 0,-1.15625 -0.09375,-1.84375 -0.296875,-2.40625 -0.5,-1.234375 -1.640625,-1.984375 -3.0625,-1.984375 -2.09375,0 -3.453125,1.59375 -3.453125,4.09375 0,2.484375 1.296875,4 3.421875,4 1.734375,0 2.921875,-0.96875 3.234375,-2.625 h -1.21875 c -0.328125,1 -1,1.515625 -1.96875,1.515625 -0.765625,0 -1.40625,-0.34375 -1.8125,-0.96875 C 1.9375,-2.1875 1.84375,-2.625 1.828125,-3.375 Z m -5.53125,-0.96875 c 0.09375,-1.40625 0.953125,-2.3125 2.15625,-2.3125 1.234375,0 2.078125,0.953125 2.078125,2.3125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-25"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13038"
           d="m 5.8125,-7.546875 v 1.09375 c -0.59375,-0.90625 -1.265625,-1.3125 -2.21875,-1.3125 -1.828125,0 -3.09375,1.703125 -3.09375,4.125 0,1.265625 0.3125,2.1875 0.953125,2.953125 0.5625,0.65625 1.28125,1.015625 2.0625,1.015625 0.90625,0 1.5625,-0.40625 2.1875,-1.34375 v 0.375 c 0,2.03125 -0.5625,2.765625 -2.0625,2.765625 C 2.625,2.125 2.09375,1.734375 1.96875,0.859375 H 0.75 c 0.109375,1.40625 1.21875,2.28125 2.859375,2.28125 1.109375,0 2.03125,-0.359375 2.53125,-0.96875 0.578125,-0.703125 0.78125,-1.640625 0.78125,-3.40625 v -6.3125 z M 3.71875,-6.65625 c 1.265625,0 1.984375,1.0625 1.984375,2.984375 0,1.828125 -0.734375,2.890625 -1.984375,2.890625 -1.234375,0 -1.96875,-1.078125 -1.96875,-2.9375 0,-1.84375 0.734375,-2.9375 1.96875,-2.9375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-26"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13041"
           d="M 1.140625,0 H 5.875 c 1,0 1.734375,-0.28125 2.296875,-0.875 C 8.6875,-1.421875 8.96875,-2.171875 8.96875,-3 8.96875,-4.265625 8.40625,-5.03125 7.0625,-5.546875 8.03125,-6 8.515625,-6.75 8.515625,-7.84375 c 0,-0.765625 -0.296875,-1.4375 -0.84375,-1.921875 C 7.109375,-10.265625 6.40625,-10.5 5.40625,-10.5 H 1.140625 Z m 1.34375,-5.984375 v -3.34375 h 2.59375 c 0.734375,0 1.15625,0.109375 1.515625,0.375 0.375,0.296875 0.578125,0.734375 0.578125,1.296875 0,0.578125 -0.203125,1.015625 -0.578125,1.296875 -0.359375,0.28125 -0.78125,0.375 -1.515625,0.375 z m 0,4.796875 V -4.796875 H 5.75 c 1.171875,0 1.890625,0.671875 1.890625,1.8125 0,1.125 -0.71875,1.796875 -1.890625,1.796875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-27"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13044"
           d="M 2.5,-10.5 H 1.15625 V 0 H 7.671875 V -1.1875 H 2.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-28"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13047"
           d="m 7.296875,-1.25 h -5.375 C 2.046875,-2.125 2.5,-2.671875 3.765625,-3.421875 l 1.4375,-0.8125 C 6.625,-5.03125 7.359375,-6.09375 7.359375,-7.375 c 0,-0.859375 -0.34375,-1.671875 -0.953125,-2.234375 -0.59375,-0.546875 -1.34375,-0.8125 -2.3125,-0.8125 -1.296875,0 -2.265625,0.46875 -2.828125,1.359375 C 0.90625,-8.515625 0.75,-7.859375 0.71875,-6.8125 H 1.984375 C 2.03125,-7.515625 2.125,-7.9375 2.296875,-8.28125 2.625,-8.921875 3.28125,-9.3125 4.046875,-9.3125 c 1.15625,0 2.015625,0.84375 2.015625,1.96875 0,0.828125 -0.46875,1.546875 -1.375,2.078125 L 3.359375,-4.5 c -2.140625,1.234375 -2.75,2.203125 -2.875,4.484375 h 6.8125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-29"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13050"
           d="m 3.296875,-10.5 -3.40625,10.78125 h 0.78125 L 4.09375,-10.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-30"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13053"
           d="m 6.734375,0 2.96875,-8.796875 V 0 H 10.96875 V -10.5 H 9.109375 L 6.046875,-1.359375 2.9375,-10.5 H 1.078125 V 0 H 2.34375 V -8.796875 L 5.328125,0 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-31"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13056"
           d="m 5.578125,-4.125 3.9375,-6.375 h -1.59375 l -3,5.109375 L 1.84375,-10.5 H 0.1875 l 4.046875,6.375 V 0 h 1.34375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-32"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13059"
           d="m 2.671875,-4.53125 h 3.46875 c 1.1875,0 1.71875,0.578125 1.71875,1.875 l -0.015625,0.9375 c 0,0.65625 0.125,1.28125 0.3125,1.71875 h 1.625 v -0.328125 c -0.5,-0.34375 -0.609375,-0.71875 -0.640625,-2.125 0,-1.71875 -0.28125,-2.25 -1.421875,-2.734375 C 8.90625,-5.78125 9.375,-6.484375 9.375,-7.6875 9.375,-9.515625 8.25,-10.5 6.1875,-10.5 H 1.34375 V 0 h 1.328125 z m 0,-1.171875 v -3.625 h 3.25 c 0.75,0 1.1875,0.125 1.515625,0.40625 0.359375,0.3125 0.546875,0.78125 0.546875,1.40625 0,1.25 -0.640625,1.8125 -2.0625,1.8125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-33"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13062"
           d="M 2.640625,-4.78125 H 7.65625 v -1.1875 H 2.640625 V -9.328125 H 8.34375 V -10.5 H 1.296875 V 0 h 1.34375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-34"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13065"
           d="m 1.28125,0 h 4.046875 c 2.65625,0 4.28125,-1.984375 4.28125,-5.265625 C 9.609375,-8.515625 8,-10.5 5.328125,-10.5 H 1.28125 Z M 2.625,-1.1875 v -8.140625 h 2.46875 c 2.078125,0 3.171875,1.40625 3.171875,4.078125 0,2.671875 -1.09375,4.0625 -3.171875,4.0625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-35"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13068"
           d="m 7.953125,-10.5 v 7.375 c 0,1.40625 -1.03125,2.28125 -2.703125,2.28125 -0.78125,0 -1.421875,-0.1875 -1.921875,-0.546875 C 2.8125,-1.796875 2.5625,-2.328125 2.5625,-3.125 V -10.5 H 1.21875 v 7.375 C 1.21875,-1 2.75,0.328125 5.25,0.328125 c 2.453125,0 4.046875,-1.34375 4.046875,-3.453125 V -10.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-36"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13071"
           d="M 5.640625,-5.390625 9.171875,-10.5 H 7.578125 L 4.875,-6.375 2.171875,-10.5 h -1.625 L 4.03125,-5.390625 0.3125,0 h 1.625 L 4.828125,-4.375 7.6875,0 h 1.65625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-37"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13074"
           d="M 4.703125,-2.515625 V 0 h 1.28125 v -2.515625 h 1.5 V -3.65625 h -1.5 v -6.765625 h -0.9375 l -4.640625,6.5625 v 1.34375 z m 0,-1.140625 h -3.1875 L 4.703125,-8.25 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-38"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13077"
           d="M 5.09375,-9.328125 H 8.546875 V -10.5 h -8.25 v 1.171875 h 3.46875 V 0 H 5.09375 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-39"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13080"
           d="m 5.640625,0 3.65625,-10.5 h -1.4375 L 4.953125,-1.609375 1.875,-10.5 H 0.4375 L 4.203125,0 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-40"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13083"
           d="m 7.171875,-7.703125 c -0.25,-1.703125 -1.34375,-2.71875 -2.890625,-2.71875 -1.125,0 -2.140625,0.546875 -2.734375,1.484375 C 0.890625,-7.90625 0.625,-6.640625 0.625,-4.75 c 0,1.75 0.234375,2.859375 0.859375,3.78125 0.546875,0.859375 1.4375,1.296875 2.5625,1.296875 1.953125,0 3.34375,-1.453125 3.34375,-3.484375 0,-1.921875 -1.296875,-3.265625 -3.125,-3.265625 -1.015625,0 -1.796875,0.375 -2.34375,1.140625 0.015625,-2.578125 0.8125,-4.015625 2.265625,-4.015625 0.890625,0 1.515625,0.578125 1.71875,1.59375 z m -3.0625,2.40625 c 1.21875,0 1.984375,0.859375 1.984375,2.25 0,1.296875 -0.859375,2.25 -2.03125,2.25 -1.1875,0 -2.078125,-0.984375 -2.078125,-2.3125 0,-1.296875 0.875,-2.1875 2.125,-2.1875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-41"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13086"
           d="m 4.09375,-4.5 h -3.4375 v 1.046875 h 3.4375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-42"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13089"
           d="M 9.3125,-10.5 H 8.03125 v 8.578125 L 2.546875,-10.5 H 1.09375 V 0 H 2.359375 V -8.515625 L 7.796875,0 H 9.3125 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-43"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13092"
           d="M 7.9375,-4.78125 V 0 H 9.28125 V -10.5 H 7.9375 v 4.53125 H 2.53125 V -10.5 H 1.203125 V 0 H 2.53125 v -4.78125 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-44"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13095"
           d="m 0.78125,3.140625 h 1.203125 v -3.9375 c 0.640625,0.78125 1.34375,1.125 2.328125,1.125 1.953125,0 3.21875,-1.5625 3.21875,-3.96875 0,-2.546875 -1.234375,-4.125 -3.234375,-4.125 -1.03125,0 -1.84375,0.46875 -2.40625,1.359375 V -7.546875 H 0.78125 Z m 3.3125,-9.78125 c 1.328125,0 2.1875,1.171875 2.1875,2.96875 0,1.71875 -0.875,2.875 -2.1875,2.875 -1.28125,0 -2.109375,-1.140625 -2.109375,-2.921875 0,-1.765625 0.828125,-2.921875 2.109375,-2.921875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-45"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13098"
           d="M 7.125,-10.5 H 5.9375 v 3.90625 C 5.4375,-7.359375 4.625,-7.765625 3.609375,-7.765625 1.65625,-7.765625 0.375,-6.1875 0.375,-3.78125 c 0,2.546875 1.234375,4.109375 3.28125,4.109375 C 4.703125,0.328125 5.421875,-0.0625 6.0625,-1 V 0 H 7.125 Z m -3.3125,3.859375 c 1.296875,0 2.125,1.140625 2.125,2.953125 0,1.75 -0.84375,2.890625 -2.109375,2.890625 C 2.5,-0.796875 1.625,-1.953125 1.625,-3.71875 c 0,-1.75 0.875,-2.921875 2.1875,-2.921875 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-46"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13101"
           d="M 6.828125,-3.15625 7.90625,0 h 1.5 L 5.71875,-10.5 H 3.984375 L 0.25,0 H 1.671875 L 2.78125,-3.15625 Z m -0.375,-1.125 H 3.109375 L 4.84375,-9.0625 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-47"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13104"
           d="M 2.796875,-10.5 H 1.4375 V 0 h 1.359375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-48"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13107"
           d="M 2.484375,-3.671875 4.1875,-5.390625 7.890625,0 h 1.59375 L 5.15625,-6.21875 9.4375,-10.5 H 7.703125 l -5.21875,5.3125 V -10.5 H 1.140625 V 0 h 1.34375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-49"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13110"
           d="M 8.375,-10.5 H 0.8125 v 1.171875 H 6.71875 L 0.40625,-1.1875 V 0 h 8 V -1.1875 H 2.09375 L 8.375,-9.296875 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-50"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13113"
           d="m 6.859375,-10.21875 h -5.28125 l -0.75,5.5625 h 1.15625 C 2.578125,-5.359375 3.0625,-5.609375 3.875,-5.609375 c 1.375,0 2.21875,0.9375 2.21875,2.453125 0,1.46875 -0.84375,2.359375 -2.234375,2.359375 -1.109375,0 -1.78125,-0.5625 -2.09375,-1.703125 H 0.5 c 0.171875,0.828125 0.328125,1.234375 0.625,1.609375 0.578125,0.78125 1.609375,1.21875 2.765625,1.21875 2.0625,0 3.5,-1.5 3.5,-3.65625 0,-2.015625 -1.34375,-3.40625 -3.296875,-3.40625 -0.71875,0 -1.296875,0.1875 -1.890625,0.625 l 0.40625,-2.84375 h 4.25 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-51"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13116"
           d="M 2.75,-1.5 H 1.25 V 0 h 1.5 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-52"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13119"
           d="M 1.015625,-10.5 V 0 h 1.1875 v -4.15625 c 0,-1.546875 0.8125,-2.5625 2.046875,-2.5625 0.40625,0 0.78125,0.125 1.0625,0.34375 0.34375,0.25 0.5,0.609375 0.5,1.140625 V 0 H 7 v -5.703125 c 0,-1.265625 -0.90625,-2.0625 -2.375,-2.0625 -1.0625,0 -1.71875,0.328125 -2.421875,1.25 V -10.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-53"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13122"
           d="M 7.6875,-3.84375 H 4.703125 v -2.984375 h -1 V -3.84375 H 0.71875 v 1 h 2.984375 v 2.984375 h 1 V -2.84375 H 7.6875 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-54"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13125"
           d="M 3.1875,-4.796875 H 3.875 c 1.390625,0 2.125,0.640625 2.125,1.90625 0,1.3125 -0.796875,2.09375 -2.109375,2.09375 C 2.5,-0.796875 1.8125,-1.5 1.734375,-3.03125 H 0.46875 c 0.046875,0.84375 0.1875,1.390625 0.4375,1.84375 0.53125,1.015625 1.53125,1.515625 2.921875,1.515625 2.109375,0 3.46875,-1.265625 3.46875,-3.234375 0,-1.328125 -0.515625,-2.046875 -1.734375,-2.484375 C 6.515625,-5.78125 6.984375,-6.5 6.984375,-7.546875 c 0,-1.78125 -1.171875,-2.875 -3.109375,-2.875 -2.0625,0 -3.15625,1.15625 -3.203125,3.359375 H 1.9375 c 0.015625,-0.625 0.078125,-0.984375 0.234375,-1.3125 0.296875,-0.578125 0.921875,-0.9375 1.71875,-0.9375 1.125,0 1.796875,0.6875 1.796875,1.8125 0,0.734375 -0.25,1.171875 -0.8125,1.421875 C 4.53125,-5.9375 4.0625,-5.875 3.1875,-5.859375 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-55"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13128"
           d="M 7.484375,-10.21875 H 0.65625 v 1.265625 H 6.1875 C 3.75,-5.484375 2.75,-3.359375 1.984375,0 H 3.34375 c 0.5625,-3.265625 1.84375,-6.078125 4.140625,-9.140625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-56"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13131"
           d="M 10.21875,-5.546875 H 5.828125 v 1.1875 H 9.03125 v 0.28125 c 0,1.875 -1.375,3.234375 -3.296875,3.234375 -1.0625,0 -2.03125,-0.390625 -2.65625,-1.078125 -0.6875,-0.75 -1.109375,-2 -1.109375,-3.296875 0,-2.578125 1.46875,-4.28125 3.6875,-4.28125 1.609375,0 2.75,0.828125 3.046875,2.1875 H 10.0625 c -0.359375,-2.140625 -1.984375,-3.359375 -4.390625,-3.359375 -1.28125,0 -2.3125,0.328125 -3.140625,1 -1.21875,1.015625 -1.890625,2.640625 -1.890625,4.53125 0,3.21875 1.96875,5.46875 4.8125,5.46875 C 6.875,0.328125 8,-0.203125 9.03125,-1.34375 L 9.359375,0.0625 h 0.859375 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-57"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13134"
           d="M 1.015625,-7.546875 V 0 H 2.21875 v -4.15625 c 0,-1.546875 0.8125,-2.5625 2.046875,-2.5625 0.953125,0 1.546875,0.578125 1.546875,1.484375 V 0 h 1.203125 v -5.703125 c 0,-1.25 -0.9375,-2.0625 -2.390625,-2.0625 -1.125,0 -1.84375,0.4375 -2.5,1.484375 v -1.265625 z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-58"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13137"
           d="m 5.609375,-10.671875 c -3.015625,0 -5.0625,2.21875 -5.0625,5.5 0,3.296875 2.03125,5.5 5.078125,5.5 1.28125,0 2.40625,-0.390625 3.25,-1.109375 1.140625,-0.96875 1.8125,-2.59375 1.8125,-4.296875 0,-3.390625 -2,-5.59375 -5.078125,-5.59375 z m 0,1.171875 c 2.265625,0 3.734375,1.71875 3.734375,4.390625 0,2.53125 -1.5,4.265625 -3.71875,4.265625 -2.25,0 -3.734375,-1.734375 -3.734375,-4.328125 C 1.890625,-7.765625 3.375,-9.5 5.609375,-9.5 Z m 0,0"
           style="stroke:none" />
      </symbol>
      <symbol
         id="glyph2-59"
         overflow="visible"
         style="overflow:visible">
        <path
           id="path13140"
           d="m 8.59375,-7.421875 c 0,-0.71875 -0.046875,-0.921875 -0.28125,-1.40625 -0.578125,-1.21875 -1.796875,-1.84375 -3.578125,-1.84375 -2.296875,0 -3.71875,1.171875 -3.71875,3.078125 0,1.28125 0.671875,2.09375 2.046875,2.453125 l 2.609375,0.6875 c 1.34375,0.34375 1.9375,0.875 1.9375,1.703125 0,0.5625 -0.3125,1.140625 -0.75,1.453125 C 6.4375,-1 5.78125,-0.84375 4.921875,-0.84375 3.78125,-0.84375 3.015625,-1.125 2.5,-1.734375 2.125,-2.1875 1.9375,-2.6875 1.953125,-3.34375 H 0.6875 c 0.015625,0.96875 0.203125,1.59375 0.625,2.171875 0.71875,1 1.921875,1.5 3.53125,1.5 1.25,0 2.265625,-0.28125 2.953125,-0.796875 0.703125,-0.5625 1.15625,-1.5 1.15625,-2.40625 0,-1.296875 -0.8125,-2.25 -2.234375,-2.640625 L 4.078125,-6.21875 C 2.8125,-6.5625 2.34375,-6.96875 2.34375,-7.78125 c 0,-1.0625 0.9375,-1.765625 2.359375,-1.765625 1.671875,0 2.59375,0.75 2.609375,2.125 z m 0,0"
           style="stroke:none" />
      </symbol>
    </g>
  </defs>
  <metadata
     id="metadata5">
    <rdf:RDF>
      <cc:Work
         rdf:about="">
        <dc:format>image/svg+xml</dc:format>
        <dc:type
           rdf:resource="http://purl.org/dc/dcmitype/StillImage" />
        <dc:title></dc:title>
      </cc:Work>
    </rdf:RDF>
  </metadata>
  <g
     transform="translate(0,-254.66665)"
     id="layer1">
    <rect
       y="254.66664"
       x="0"
       height="42.333332"
       width="171.97917"
       id="rect29"
       style="fill:#ffffff;fill-opacity:1;stroke:none;stroke-width:0.20445883;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
  </g>
  <g
     transform="translate(0,-89.958333)"
     id="layer2">
    <flowRoot
       transform="translate(160.2619,-225.08482)"
       xml:space="preserve"
       id="flowRoot1183"
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:13.33333302px;line-height:1;font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#000000;fill-opacity:1;stroke:none"><flowRegion
         id="flowRegion1185"><rect
           id="rect1187"
           width="1.2069778"
           height="15.690712"
           x="75.436111"
           y="556.19049" /></flowRegion><flowPara
         id="flowPara1189" /></flowRoot>    <text
       xml:space="preserve"
       style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;font-size:3.52777767px;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#ffffff;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       x="182.5074"
       y="-33.97517"
       id="text329"><tspan
         id="tspan327"
         x="182.5074"
         y="-33.97517"
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332">Unadjusted</tspan><tspan
         x="182.5074"
         y="-30.094614"
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332"
         id="tspan331">RNA data</tspan></text>
    <text
       id="text252"
       y="-33.97517"
       x="226.26772"
       style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;font-size:3.52777767px;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#ffffff;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       xml:space="preserve"><tspan
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332"
         y="-33.97517"
         x="226.26772"
         id="tspan248">Adjusted</tspan><tspan
         id="tspan250"
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332"
         y="-30.094614"
         x="226.26772">RNA data</tspan></text>
    <text
       xml:space="preserve"
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:4.23333311px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#000000;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       x="218.26079"
       y="-31.358486"
       id="text3351"><tspan
         id="tspan3349"
         x="218.26079"
         y="-27.743219"
         style="stroke-width:0.26458332" /></text>
    <text
       xml:space="preserve"
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:4.23333311px;line-height:1.25;font-family:sans-serif;-inkscape-font-specification:'sans-serif, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#000000;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       x="311.44803"
       y="-128.11108"
       id="text178"><tspan
         id="tspan176"
         x="311.44803"
         y="-124.36558"
         style="stroke-width:0.26458332" /></text>
    <flowRoot
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:13.33333302px;line-height:1;font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#000000;fill-opacity:1;stroke:none"
       id="flowRoot1183-1"
       xml:space="preserve"
       transform="translate(382.39372,-235.50136)"><flowRegion
         id="flowRegion1185-9"><rect
           y="556.19049"
           x="75.436111"
           height="15.690712"
           width="1.2069778"
           id="rect1187-4" /></flowRegion><flowPara
         id="flowPara1189-7" /></flowRoot>    <text
       id="text329-8"
       y="-44.39172"
       x="404.63922"
       style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;font-size:3.52777767px;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#ffffff;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       xml:space="preserve"><tspan
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332"
         y="-44.39172"
         x="404.63922"
         id="tspan327-4">Unadjusted</tspan><tspan
         id="tspan331-5"
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332"
         y="-40.511166"
         x="404.63922">RNA data</tspan></text>
    <text
       xml:space="preserve"
       style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;font-size:3.52777767px;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#ffffff;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       x="448.39954"
       y="-44.39172"
       id="text252-0"><tspan
         id="tspan248-3"
         x="448.39954"
         y="-44.39172"
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332">Adjusted</tspan><tspan
         x="448.39954"
         y="-40.511166"
         style="font-style:normal;font-variant:normal;font-weight:bold;font-stretch:normal;line-height:1.10000002;font-family:'Nimbus Sans L';-inkscape-font-specification:'Nimbus Sans L Bold';text-align:center;text-anchor:middle;fill:#ffffff;stroke-width:0.26458332"
         id="tspan250-6">RNA data</tspan></text>
    <text
       id="text3351-6"
       y="-41.775036"
       x="440.39261"
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:4.23333311px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#000000;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       xml:space="preserve"><tspan
         style="stroke-width:0.26458332"
         y="-38.159771"
         x="440.39261"
         id="tspan3349-3" /></text>
    <text
       id="text2854"
       y="-128.22043"
       x="339.50894"
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:4.23333311px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#000000;fill-opacity:1;stroke:none;stroke-width:0.26458332"
       xml:space="preserve"><tspan
         style="stroke-width:0.26458332"
         y="-124.60516"
         x="339.50894"
         id="tspan2852" /></text>
    <g
       transform="matrix(0.3159036,0,0,0.3159036,-64.910107,90.359885)"
       id="g887">
      <path
         id="path94"
         d="m 524.84054,71.575175 c -0.43311,-5.932451 -21.36876,-14.585386 -47.22528,-2.851408 -2.68203,1.217136 -5.76235,1.39478 -8.66362,2.533866 1.41618,0.912559 -0.76378,3.052972 -0.23751,2.551564 1.37653,-1.311515 6.56248,-2.884787 8.58222,-1.51651 28.71353,19.452075 47.97032,5.348276 47.54419,-0.717512 z"
         style="fill:#e7cbca;fill-opacity:1;stroke:none;stroke-width:0.15337786px;stroke-linecap:butt;stroke-linejoin:miter;stroke-opacity:1" />
      <path
         style="fill:#6c5d53;fill-opacity:0.78431373;stroke:none;stroke-width:1.19728899;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
         d="m 430.93491,1.3528154 c 4.25013,-1.55399239 32.6067,11.5076446 30.56357,53.2798726 -0.3079,6.295094 9.36194,15.938708 10.42081,17.726999 0.40027,0.676074 -2.45951,0.425612 -2.72391,1.173304 -2.6782,-1.640157 -9.00632,-14.911175 -11.4828,-16.181673 C 423.3284,39.71135 426.9999,2.7630497 430.93492,1.3528088 Z"
         id="path92" />
      <path
         id="path80"
         style="fill:#918ebe;fill-opacity:1;stroke:#ffffff;stroke-width:1.32291663;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
         d="m 485.10948,106.28175 c 0,0 -14.15967,-33.306723 -12.68766,-35.945381 1.472,-2.638657 19.45308,-16.752464 19.45308,-16.752464 l -7.64163,-6.960826 c 0,0 -12.46658,19.099595 -15.57167,21.947594 -3.1051,2.847999 -46.35299,10.415468 -46.35299,10.415468 l 9.7669,21.095389 c 0,0 34.39874,-27.143412 35.62666,-24.971947 1.22792,2.171464 5.28298,33.304807 5.28298,33.304807 z" />
      <path
         style="fill:#ebadff;fill-opacity:1;stroke:#ffffff;stroke-width:1.32291663;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
         d="m 493.9447,126.81357 c -7.11424,4.6343 -11.88321,4.84438 -20.95137,2.13822 -19.81116,-9.80533 -13.61314,-35.495623 -0.21756,-39.72234 13.39558,-4.226719 24.398,1.620676 28.35893,10.93884 3.96094,9.31817 -0.0757,22.01099 -7.19,26.64528 z"
         id="path36" />
      <path
         style="fill:#890a71;fill-opacity:0.57843137;stroke:none;stroke-width:0.28116623;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         d="m 490.09784,124.99658 c -2.85624,3.24207 -15.3735,1.35186 -15.87461,-1.14947 -1.68935,-3.00507 1.10023,-12.84586 4.8268,-14.07055 2.7585,-2.89052 15.76963,-0.27577 16.55867,2.14723 1.64668,2.4778 -1.95933,12.1023 -5.51086,13.07279 z m -0.32253,-0.42959 c -3.26552,-3.17095 -1.04847,-5.8045 4.66899,-11.70335 -5.64544,2.79196 -10.83529,4.81336 -14.80116,-1.13556 2.62991,4.00551 0.44741,7.29883 -3.94777,11.41338 -0.2359,0.0907 -0.47619,0.18705 -0.72124,0.28997 0.24842,-0.0961 0.48818,-0.1928 0.72124,-0.28997 6.94744,-1.11856 10.13746,-0.046 14.07994,1.42553 z"
         id="rect51" />
      <path
         style="fill:#ee93fd;fill-opacity:1;stroke:#ffffff;stroke-width:1.32291663;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
         d="m 450.9714,108.56581 c 7.59705,-11.772433 11.26758,-24.959531 0.32371,-39.344596 -10.94388,-14.385065 -38.36337,-13.104521 -48.1698,2.153156 -9.80644,15.257677 -8.27748,29.48217 3.16122,39.71368 11.43869,10.23154 34.46073,9.48175 44.68487,-2.52224 z"
         id="path40" />
      <path
         id="path58"
         d="m 432.39443,101.72157 c -3.05438,2.34677 -6.07482,5.82708 -8.05618,4.87554 -4.90768,1.34839 -15.46644,-9.647281 -14.57389,-13.130879 -4.15475,-0.564182 9.61676,-19.5093 13.69916,-16.143113 3.54749,-2.772271 15.48998,8.333232 14.12088,12.927908 1.24075,2.843906 -0.54283,7.900009 -5.18997,11.470544 z m -8.01481,4.41387 c -1.22417,-11.148949 5.05714,-13.119033 12.94075,-15.820888 -6.54471,-4.697394 -12.62594,-2.251853 -13.97512,-12.532558 -1.11025,6.932898 -3.52276,13.206181 -12.01549,15.865475 -0.29971,-0.02135 -0.41202,-0.07439 -0.72949,-0.08233 0.31603,0.02152 0.42805,0.07361 0.72949,0.08233 7.97564,0.552802 9.32048,7.152671 13.04986,12.487971 z"
         style="fill:#803766;fill-opacity:1;stroke:none;stroke-width:0.27449244;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <path
         style="fill:#ebadff;fill-opacity:1;stroke:#ffffff;stroke-width:1.32291663;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
         d="m 474.7348,64.48489 c 12.71219,9.742455 26.39644,1.6764 29.00579,-8.547708 1.87847,-7.584606 -4.31727,-16.491395 -11.65721,-18.770246 -19.25351,-5.293294 -27.07011,16.275467 -17.34858,27.317954 z"
         id="path38" />
      <path
         id="path60"
         d="m 499.25123,41.685619 c -0.73638,-4.358676 -9.1967,-4.673336 -11.31061,-2.308633 -1.80286,1.559231 -1.9883,8.554986 0.36615,10.133184 1.09045,2.509312 9.55485,3.835772 11.78258,1.732368 1.815,-1.565124 0.75966,-10.142418 -0.83816,-9.556917 z m -0.69171,0.462434 c -2.93996,1.328676 -1.62541,3.687184 1.15655,8.676899 -2.88315,-5.666542 -6.3088,-6.909296 -10.59109,-2.434989 3.33926,-3.16174 3.37898,-7.268591 -0.40447,-8.13514 -0.14636,-0.108317 -0.29457,-0.221188 -0.44478,-0.33926 0.15401,0.114452 0.30175,0.227417 0.44478,0.33926 4.96484,1.993106 6.08623,1.136265 9.83901,1.89323 z"
         style="fill:#b048b2;fill-opacity:1;stroke:none;stroke-width:0.2811662;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <g
         aria-label="Allspice"
         style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;line-height:1.25;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#4d4d4d;fill-opacity:1;stroke:none;stroke-width:0.26458332"
         id="text825">
        <path
           d="m 468.643,4.5745775 h 1.10795 l 5.03535,12.1212235 h -1.24024 l -1.52135,-3.671094 h -5.45703 l -1.43867,3.671094 h -1.21543 z m 0.57051,1.6784504 q -0.55397,1.4304036 -1.10794,2.8277342 -0.5457,1.3890629 -1.09141,2.8029299 h 4.53099 z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path852" />
        <path
           d="M 477.48174,4.5828457 V 16.695801 h -1.14102 V 4.5828457 Z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path854" />
        <path
           d="M 481.343,4.5828457 V 16.695801 h -1.14101 V 4.5828457 Z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path856" />
        <path
           d="m 489.05726,10.188705 q -0.008,-0.570508 -0.63665,-0.9260418 -0.62839,-0.3555339 -1.55443,-0.3555339 -0.92604,0 -1.42214,0.2480469 -0.48782,0.2480468 -0.69453,0.4878255 -0.2067,0.2397786 -0.2067,0.6614583 0,0.42168 0.80201,0.785482 0.47129,0.214974 1.4056,0.429948 2.79466,0.644921 3.3569,1.554427 0.28939,0.46302 0.22325,1.058333 0.16536,1.182357 -1.26504,2.091862 -1.08314,0.677994 -2.33164,0.677994 -1.24024,0.0083 -2.38125,-0.851627 -1.14929,-0.859896 -1.14929,-1.976107 h 1.14102 q 0,0.661459 0.79375,1.174089 0.80202,0.51263 1.67018,0.51263 0.86817,0 1.62884,-0.396875 0.24805,-0.14056 0.53744,-0.479557 0.28939,-0.347266 0.21497,-0.752409 0.14056,-0.578776 -0.63665,-0.917774 -0.48783,-0.223242 -1.43867,-0.438216 -0.94258,-0.23151 -1.55443,-0.396875 -0.61185,-0.165364 -1.09141,-0.429948 -1.0666,-0.595312 -1.0666,-1.728059 0,-1.1327477 1.05833,-1.794206 1.05834,-0.6614582 2.43086,-0.6614582 1.37253,0 2.33991,0.6697265 0.96738,0.6697265 0.96738,1.7528647 z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path858" />
        <path
           d="m 492.48031,7.9232101 h 1.14101 v 1.0583333 q 1.05007,-0.8516276 1.5875,-1.0335286 0.53744,-0.181901 0.93431,-0.1901693 1.68672,0.00827 2.69544,1.4138671 1.00873,1.4055994 1.00873,3.1998044 0,1.794206 -0.83509,3.050977 -0.96739,1.471744 -2.7864,1.471744 -1.81901,0 -2.60449,-0.868164 v 4.043164 h -1.14101 z m 5.53971,2.0505207 q -0.68626,-1.0748697 -1.90996,-1.0748697 -1.2237,0 -2.48874,1.7197919 v 3.464388 q 0.57051,1.058333 1.7446,1.504817 0.42994,0.165365 0.8847,0.165365 0.46302,0 0.80202,-0.14056 0.34726,-0.14056 0.73587,-0.487826 0.39687,-0.347265 0.66146,-1.099674 0.25631,-0.760677 0.25631,-1.86862 0,-1.107942 -0.68626,-2.1828122 z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path860" />
        <path
           d="m 503.08844,7.9149419 v 8.7891271 h -1.14101 V 7.9149419 Z M 501.94743,6.2612961 V 4.5828457 h 1.14101 v 1.6784504 z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path862" />
        <path
           d="m 511.39802,10.577312 q 0.008,-0.7937504 -0.66973,-1.2319666 -0.678,-0.4382161 -1.63711,-0.4382161 -1.00872,0 -1.90169,0.9095052 -0.89297,0.9095055 -0.89297,2.5548825 0,1.645378 0.74414,2.52181 0.74414,0.876432 1.98437,0.876432 1.24024,0 1.81075,-0.537435 0.5705,-0.537435 0.56224,-1.107942 h 1.14101 q -0.008,0.942578 -0.76894,1.769401 -0.93431,1.008723 -2.67891,1.008723 -2.80293,0 -3.64629,-2.554882 -0.28939,-0.876432 -0.28939,-2.033984 0,-1.157552 0.38034,-1.992644 0.38034,-0.8433589 0.95912,-1.4055985 0.58704,-0.5705077 1.2733,-0.8598957 0.69453,-0.289388 1.71979,-0.289388 1.03353,0 2.04226,0.7276041 1.00872,0.7276041 1.00872,2.0835941 z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path864" />
        <path
           d="m 514.79625,12.627832 q 0.11576,1.35599 0.89297,2.248958 0.77722,0.892969 2.02572,0.884701 1.14928,-0.0083 1.90996,-0.669727 0.31419,-0.264583 0.45475,-0.537434 0.14883,-0.28112 0.14883,-0.438217 h 1.14102 q 0.008,0.719336 -0.86817,1.653646 -1.0666,1.132747 -2.42259,1.132747 -1.34772,0 -2.1084,-0.37207 -0.75241,-0.380338 -1.2733,-1.02526 -1.05834,-1.30638 -1.05834,-3.224609 0,-1.918229 1.0418,-3.2163413 1.0418,-1.2981119 2.96003,-1.2981119 1.91822,0 2.96002,1.2485025 1.0418,1.2402347 1.0418,3.6132157 z m 5.67201,-1.141015 q -0.28939,-2.5796877 -2.93522,-2.5796877 -1.10794,0 -1.81901,0.7441406 -0.71107,0.7441401 -0.8847,1.8355471 z"
           style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:16.93333244px;font-family:AnjaliOldLipi;-inkscape-font-specification:AnjaliOldLipi;fill:#4d4d4d;fill-opacity:1;stroke-width:0.26458332"
           id="path866" />
      </g>
    </g>
    <text
       id="text2069"
       y="129.65414"
       x="12.249987"
       style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:4.14235115px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:start;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:start;fill:#4d4d4d;fill-opacity:1;stroke:none;stroke-width:0.08629897"
       xml:space="preserve"><tspan
         style="font-size:4.14235115px;fill:#4d4d4d;stroke-width:0.08629897"
         y="129.65414"
         x="12.249987"
         id="tspan2067">mRNA-seq</tspan></text>
    <g
       style="fill:#ce6a2a;fill-opacity:1"
       transform="matrix(0.28148654,0,0,0.38790612,-1.4186311,89.236646)"
       id="g5513">
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5397"
         width="54.545269"
         height="4.0908952"
         x="13.825336"
         y="46.84251" />
      <rect
         y="40.09288"
         x="20.574968"
         height="4.0908952"
         width="54.545269"
         id="rect5399"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5401"
         width="54.545269"
         height="4.0908952"
         x="34.074234"
         y="73.841057" />
      <rect
         y="67.091415"
         x="40.823864"
         height="4.0908952"
         width="54.545269"
         id="rect5403"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5405"
         width="54.545269"
         height="4.0908952"
         x="47.573498"
         y="53.592136" />
      <rect
         y="60.34177"
         x="67.822403"
         height="4.0908952"
         width="54.545269"
         id="rect5407"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5409"
         width="54.545269"
         height="4.0908952"
         x="7.0757051"
         y="80.590675" />
      <rect
         y="67.0914"
         x="101.57056"
         height="4.0908952"
         width="54.545269"
         id="rect5411"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5413"
         width="54.545269"
         height="4.0908952"
         x="94.820923"
         y="73.841042" />
      <rect
         y="80.590668"
         x="67.822395"
         height="4.0908952"
         width="54.545269"
         id="rect5415"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5417"
         width="54.545269"
         height="4.0908952"
         x="34.07423"
         y="87.340294" />
      <rect
         y="33.343246"
         x="-149.3662"
         height="4.0908952"
         width="54.545269"
         id="rect5419"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         transform="scale(-1,1)" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5421"
         width="54.545269"
         height="4.0908952"
         x="-142.61655"
         y="87.340363"
         transform="scale(-1,1)" />
      <rect
         y="26.593597"
         x="-129.11729"
         height="4.0908952"
         width="54.545269"
         id="rect5423"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         transform="scale(-1,1)" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5425"
         width="54.545269"
         height="4.0908952"
         x="-122.36766"
         y="5.6697354"
         transform="scale(-1,1)" />
      <rect
         y="13.094329"
         x="-115.61803"
         height="4.0908952"
         width="54.545269"
         id="rect5427"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         transform="scale(-1,1)" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5429"
         width="54.545269"
         height="4.0908952"
         x="-95.369125"
         y="19.843964"
         transform="scale(-1,1)" />
      <rect
         y="40.09288"
         x="-156.11583"
         height="4.0908952"
         width="54.545269"
         id="rect5431"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         transform="scale(-1,1)" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5433"
         width="54.545269"
         height="4.0908952"
         x="-61.620968"
         y="26.593603"
         transform="scale(-1,1)" />
      <rect
         y="60.341797"
         x="-68.370598"
         height="4.0908952"
         width="54.545269"
         id="rect5435"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         transform="scale(-1,1)" />
      <rect
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         id="rect5437"
         width="54.545269"
         height="4.0908952"
         x="-95.369125"
         y="33.343246"
         transform="scale(-1,1)" />
      <rect
         y="46.842522"
         x="-129.11729"
         height="4.0908952"
         width="54.545269"
         id="rect5439"
         style="fill:#ce6a2a;fill-opacity:1;stroke:#ffffff;stroke-width:0.6756382;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1"
         transform="scale(-1,1)" />
    </g>
    <g
       transform="matrix(0.35710458,0,0,0.35710458,-16.552211,86.299641)"
       id="g5561">
      <g
         id="g5395"
         transform="matrix(1.2231511,0,0,1.0342076,53.092274,-3.221107)">
        <path
           style="fill:#ff45bd;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,37.902172 h 3.41634 v -9.115606 h -3.41634 z m 0,0"
           id="path13543" />
        <path
           style="fill:#ff3f54;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,48.786372 h 3.41634 v -9.115617 h -3.41634 z m 0,0"
           id="path13547" />
        <path
           style="fill:#ff5e23;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,59.670563 h 3.41634 v -9.115582 h -3.41634 z m 0,0"
           id="path13551" />
        <path
           style="fill:#f59411;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,70.554798 h 6.06217 v -9.115625 h -6.06217 z"
           id="path13555" />
        <path
           style="fill:#dcd400;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,81.438998 h 3.41634 v -9.115589 h -3.41634 z m 0,0"
           id="path13559" />
        <path
           style="fill:#6eeb23;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,92.323231 h 3.41634 v -9.115619 h -3.41634 z m 0,0"
           id="path13563" />
        <path
           style="fill:#28d982;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,103.20743 h 3.41634 v -9.115623 h -3.41634 z m 0,0"
           id="path13567" />
        <path
           style="fill:#0faede;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.45891759"
           d="m 276.99832,114.0916 h 36.40689 v -9.11559 h -36.40689 z m 0,0"
           id="path13571" />
        <path
           style="fill:#217fff;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 276.99832,124.97579 h 3.41634 v -9.11558 h -3.41634 z m 0,0"
           id="path13575" />
        <path
           id="path5312"
           d="m 319.33168,37.902172 h 3.41634 v -9.115606 h -3.41634 z m 0,0"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5314"
           d="m 319.33168,48.786372 h 3.41634 v -9.115617 h -3.41634 z m 0,0"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5316"
           d="m 319.33168,59.670563 h 3.41634 v -9.115582 h -3.41634 z m 0,0"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5318"
           d="m 319.33168,70.554798 h 35.16634 v -9.115625 h -35.16634 z"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5320"
           d="m 319.33168,81.438998 h 3.41634 v -9.115589 h -3.41634 z m 0,0"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5322"
           d="m 319.33168,92.323231 h 9.23717 v -9.115619 h -9.23717 z"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5324"
           d="m 319.33168,103.20743 h 3.41634 v -9.115623 h -3.41634 z m 0,0"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           id="path5326"
           d="m 319.33168,114.0916 h 3.41503 v -9.11559 h -3.41503 z"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.45891759" />
        <path
           id="path5328"
           d="m 319.33168,124.97579 h 3.41634 v -9.11558 h -3.41634 z m 0,0"
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,115.86019 h 3.41634 v 9.1156 h -3.41634 z m 0,0"
           id="path5330" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,104.97599 h 4.24237 v 9.11562 h -4.24237 z"
           id="path5332" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,94.091797 h 3.41634 v 9.115583 h -3.41634 z m 0,0"
           id="path5334" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,83.207562 h 24.2433 v 9.115625 h -24.2433 z"
           id="path5336" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,72.323362 h 3.41634 v 9.115589 h -3.41634 z m 0,0"
           id="path5338" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,61.439129 h 3.41634 v 9.115619 h -3.41634 z m 0,0"
           id="path5340" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,50.55493 h 3.41634 v 9.115623 h -3.41634 z m 0,0"
           id="path5342" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.45891759"
           d="m 361.66504,39.67076 h 4.13495 v 9.11559 h -4.13495 z"
           id="path5344" />
        <path
           style="fill:#808080;fill-opacity:0.70196096;fill-rule:nonzero;stroke:none;stroke-width:0.74817562"
           d="m 361.66504,28.78657 h 3.41634 v 9.11558 h -3.41634 z m 0,0"
           id="path5346" />
      </g>
      <text
         xml:space="preserve"
         style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:9.87777805px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#666666;fill-opacity:1;stroke:none;stroke-width:0.26458332"
         x="393.85269"
         y="21.642082"
         id="text5517"><tspan
           id="tspan5515"
           x="393.85269"
           y="21.642082"
           style="font-size:9.87777805px;text-align:center;text-anchor:middle;fill:#666666;stroke-width:0.26458332">Subtypes</tspan></text>
      <text
         id="text5521"
         y="21.642082"
         x="445.52206"
         style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:9.87777805px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#666666;fill-opacity:1;stroke:none;stroke-width:0.26458332"
         xml:space="preserve"><tspan
           style="font-size:9.87777805px;text-align:center;text-anchor:middle;fill:#666666;stroke-width:0.26458332"
           y="21.642082"
           x="445.52206"
           id="tspan5519">Drivers</tspan></text>
      <text
         xml:space="preserve"
         style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:9.87777805px;line-height:1.25;font-family:'Nimbus Sans';-inkscape-font-specification:'Nimbus Sans, Normal';font-variant-ligatures:normal;font-variant-caps:normal;font-variant-numeric:normal;font-feature-settings:normal;text-align:center;letter-spacing:0px;word-spacing:0px;writing-mode:lr-tb;text-anchor:middle;fill:#666666;fill-opacity:1;stroke:none;stroke-width:0.26458332"
         x="497.38028"
         y="21.642082"
         id="text5525"><tspan
           id="tspan5523"
           x="497.38028"
           y="21.642082"
           style="font-size:9.87777805px;text-align:center;text-anchor:middle;fill:#666666;stroke-width:0.26458332">Tissues</tspan></text>
    </g>
    <path
       id="path5563"
       d="m 47.093837,108.94591 h 4.736834 v -1.75769 l 5.236444,3.12196 -5.240514,2.97101 v -1.61947 h -4.732764 z"
       style="fill:none;stroke:#666666;stroke-width:0.34519589;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1" />
    <path
       style="fill:none;stroke:#666666;stroke-width:0.34519589;stroke-linecap:round;stroke-linejoin:round;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
       d="m 106.09962,108.94591 h 4.73683 v -1.75769 l 5.23645,3.12196 -5.24052,2.97101 v -1.61947 h -4.73276 z"
       id="path5567" />
  </g>
</svg>

``` {r echo=FALSE, results="hide"}
opt <- options(digits=3)
set.seed(1)
```

# Getting started

You can install Allspice using the standard procedure:

``` {r eval=FALSE}
# Install the package from a remote repository.
install.packages("Allspice")
```

To activate and list the library functions, type

``` {r}
# Activate the library.
library("Allspice")
packageVersion("Allspice")
ls("package:Allspice")
```

Each Allspice function comes with a help page that contains a code example,
such as

``` {r eval=FALSE}
# Access function documentation (not shown in vignette).
? Allspice::classifier
```

You can run all the code examples in one go by typing

``` {r eval=FALSE}
# Run all code examples (not shown in vignette).
fn <- system.file("examples.R", package = "Allspice")
source(fn)
```


# Dataset

To run this tutorial, we will use simulated data that mimics B-cell
acute lymphoblast leukemia samples:

``` {r}
# Generate gene RNA read counts.
simu <- bcellALL(300)
print(simu$counts[1:5,1:6])
print(simu$metadata[1:6,])
```

The output contains the unadjusted read counts as would be produced by
a standard RNA-seq pipeline and patients' sex and age are also simulated.
Please note that these data are artificial and meant only for demonstration
purposes; they do not reflect the complex biology of ALL accurately.

The read counts must be stored in a matrix that has the samples organized
into columns and the genes are listed as rows. For the meta-data, patients
can be listed in rows as that is more convenient in most situations.


# Classify samples {.tabset}

## Predict labels

The first step is to create a new classifier:

``` {r}
# Set up a classifier for genetic B-cell ALL subtypes.
cls <- classifier()
```

By default, the command creates an object that contains three models:
i) ALL subtype prediction, ii) driver gene prediction and iii) tissue
profiling to make sure the RNA data are suitable for analyses.

The next step is to import the covariates (e.g. sex and age) into the
classifier. If there are no covariate data available, this step can be
skipped. The default classifier uses MALE and AGE as column headings,
see the format of the metadata in the first section of the vignette. The
names of covariates are also available as

``` {r}
# List covariates.
info <- information(cls)
print(info$covariates[,c("ASSET","TITLE","COVAR")])
```

To set the covariates, use the command

``` {r}
# Set covariates.
covariates(cls) <- simu$metadata
```

Missing values or incomplete data are allowed, however, a warning will be
produced when the subtypes are predicted. Also, it is important to set the
covariates **before** loading the RNA read counts.

Once the covariates have been set, the RNA-seq read counts are next:

``` {r}
# Load RNA-seq profiles.
profiles(cls) <- simu$counts
```

The above command pre-processes the data and predicts the subtypes based on
the combined information from covariates and read counts. To get the results,
use the command

``` {r}
# Prediction results.
pred <- predictions(cls)
primary <- pred[[1]]
print(primary[1:6,c("LABEL","FREQ","PROX","EXCL")])
```

The output is a list of data frames, where each element contains the results
generated by a classification asset (see the section on how to create your own
classifier for more information on assets). Here, we are interested in the ALL
subtype which is the primary asset in the classifier.

Please use the tabs at the top to navigate to the next page.

## Metrics

Here are selected results from the previous page again:
``` {r}
# Prediction results.
ambig <- which(primary$CATEG == "Ambiguous")
uncla <- which(primary$CATEG == "Unclassified")
rows <- unique(c(1:5, ambig[1], uncla[1]))
print(primary[rows,c("LABEL","MATCH","FREQ","PROX","EXCL")])
```

The data frame includes additional information besides the most plausible
ALL subtype **LABEL**. The ALL subtype that most resembles the patient's
profile is defined as the best-matching subtype **MATCH**. For most cases,
LABEL will refer to the same subtype as MATCH, but failure to pass quality
checks and the rarity of a subtype may sometimes lead to conflicting
results.

The next column named **FREQ** tells the frequency of the predicted subtype
given the observed RNA profile and covariates. For example, if FREQ is 0.9,
then you would expect to see 9 out of 10 patients that share this data profile
to have that predicted ALL subtype. This metric depends on the training set
that was used when the classification asset was created. Thus rare subtypes
are likely to get lower frequency estimates even if the RNA profile would be
a close match.

The frequency metric does not capture mutual exclusivity because it is
evaluated independently for each subtype. For example, Allspice allows
patients to have more than one subtype in parallel when the statistical model
is trained. In this scenario, parallel subtypes may all get high frequencies,
of which the highest would be chosen as the predicted subtype. To identify
samples with mixed transcriptional characteristics, the results also includes
a probabilistic estimate for exclusivity in the column **EXCL** that tells
how likely it is that a sample comes from a single ALL subtype.

**PROX** (proximity) and **EXCL** (exclusivity) are used as quality metrics.
By default, Allspice labels any samples with <50% proximity as
'Unclassified'. Of those that pass the probability threshold, samples
with <50% exclusivity are labelled as 'Ambiguous'. The proximity measure
is conceptually the same as subtype frequency, however, any differences
in subtype prevalence are adjusted away.

You may have noticed that the subtype labels and the matched subtype
names are slightly different. This is because text labels with
non-alphanumeric characters may be automatically changed by R when used as
row or column names in data structures, thus the subtype identities are
made safe compared to the human readable labels. You can access
subtype labels by typing:

``` {r}
# Access subtype labelling information.
info <- information(cls)
print(info$categories[1:5,c("ASSET","TITLE","CATEG","LABEL")])
```

See also the Iris data example in the section on creating new classifiers.
It contains instructions on how to set the labels for a classification asset.

Please use the tabs at the top to navigate to the next page.

## Visual report

Detailed classification results can be visualised on a case-by-case basis.
In the first example, we first identify a patient sample that passed quality
control and did not show mixed characteristics:

``` {r}
# Select successful classification.
rows <- which((primary$CATEG != "Ambiguous") & (primary$FREQ > 0.9))
print(primary[rows[1],c("LABEL","MATCH","FREQ","PROX","EXCL")])
```

``` {r results="hide", fig.width=8, fig.height=6, fig.align="center", fig.cap="Figure: Classification results. The predicted subtype label is written on the top left corner. The expected frequency of the subtype given the data profile is written as a percentage after the predicted label. RNA biomarker scores were also calculated for the presence of alterations in specific genes (center bar chart), note that a patient may have multiple driver genes in parallel. The right-most chart shows RNA biomarker scores for the predicted source tissue of the sample (in this simulated dataset, all samples were generated from B-cell ALL profiles). "}
# Show patient report.
report(cls, name = rows[1], file = NULL)
```

The second example shows a case where the subtype is less obvious due to mixed
transcriptional characteristics. Sometimes this can be caused by random
incidental fluctuations that are always present in biological data, but some
of these cases will be "real" in the sense that the same individual can
harbour multiple cancer driving mutations or some alterations affect wide
regions of the genome (e.g. deletions or duplications of chromosomal
segments) and thus multiple genes would be involved.

``` {r}
# Select ambiguous classification.
rows <- which((primary$CATEG == "Ambiguous") & (primary$PROX > 0.9))
print(primary[rows[1],c("LABEL","MATCH","FREQ","PROX","EXCL")])
```

Mixed profiles typically manifest multiple indicators for driver genes while
still being identified as a B-cell ALL tissue type:

``` {r results="hide", fig.width=8, fig.height=6, fig.align="center", fig.cap="Figure: Classification results for a case with mixed transcriptional characteristics."}
# Show patient report.
report(cls, name = rows[1], file = NULL)
```

Lastly, the simulated dataset includes samples with randomized data:

``` {r}
# Select poor quality samples.
rows <- which(primary$CATEG == "Unclassified")
print(primary[rows[1],c("LABEL","MATCH","FREQ","PROX","EXCL")])
```

``` {r results="hide", fig.width=8, fig.height=6, fig.align="center", fig.cap="Figure: Classification results for a case with atypical data."}
# Show patient report.
report(cls, name = rows[1], file = NULL)
```


# Train new classifier {.tabset}

## Configuration

In Allspice, a classifier is actually a collection of classification models.
These models are enclosed in classification *assets* (objects of the Asset
class). As was observed in the previous sections, the default Allspice
classifier contains three assets (ALL subtypes,  driver genes and tissues).
This section describes how to create a new RNA-seq classification asset from
the simulated B-cell ALL dataset. Another example that uses the classisal
Iris flower dataset is also presented as a demonstration on how to use
Allspice for any type of dataset with category labels.

Before creating the assets, it is important to configure the models for
different types of datasets. The default configuration is shown below:

``` {r}
# Create a new empty asset.
bALL <- asset()
print(configuration(bALL))
```

RNA-seq normalization parameters include **norm** (if set to 0,
normalization is not performed), **nonzero.min** (the minimum read
count considered non-neglible expression) and **nonzero.ratio**
(minimum ratio of non-neglible values for a transcript to be included
in the output). Allspice uses the DESeq2 method for the normalization
of read counts (Genome Biol 15, 550, 2014).

Standardization parameters include **standard** (if set to 0,
standardization is not performed) and **logarithm** (if set to 0,
data values are used without taking the logarithm). The exact
logarithmic transformation is log2(x + 1).

Feature selection parameters include **ninput.max** (the maximum
number of features to be used for classification) and
**rrinput.max** (the maximum correlation r-squared to be allowed
between features).

Classification parameters include **proximity.min** (minimum
similarity rating considered for reliable classification) and
**exclusivity.min** (minimum exclusivity for non-ambiguous
classification).

Only empty assets can be re-configured. To change the parameters,
use a numeric vector with appropriately named elements:

``` {r}
# Re-configure asset.
configuration(bALL) <- c(ninput.max=30, nonzero.min=90)
print(configuration(bALL)[c("ninput.max","nonzero.min")])
```

Please use the tabs at the top to navigate to the next page.

## RNA-seq

To populate an empty asset, some data organization is required. The first
thing to decide is the title of the asset, which will be displayed in
the visual report (see figures in the previous section). The process begins
with a list:

``` {r}
# Prepare asset title.
materials <- list(title="Simutypes")
```

Next, non-normalized RNA data are included. The dataset needs to be a
numerical matrix with samples in columns:

``` {r}
# Prepare RNA-seq read counts.
materials$dat <- simu$counts
```

Covariates can be in a data frame or a matrix with samples on rows, just
make sure all the columns are numeric:

``` {r}
# Prepare covariate data.
materials$covariates <- simu$metadata[,c("MALE","AGE")]
```

It is very important that all the rows and columns are named in each
data structure since they will be used later to link the inputs together.
It is good practice to always ensure that the row and column names
are written with alphanumeric characters without white spaces, otherwise
the automatic R filters may change some of the characters and cause
unexpected errors.

The last remaining source of information are the pre-defined subtypes
themselves that will be used to train the classification model. In this
example, the subtypes are mutually exclusive (a patient can only exhibit a
single subtype), therefore the subtypes can be obtained from the single
column in the metadata:

``` {r}
# Prepare subtype information.
categ <- simu$metadata[,"SUBTYPE",drop=FALSE]
rows <- which(categ != "Contaminated")
materials$bits <- categ[rows,,drop=FALSE]
```

Note the drop flag in the code above; this ensures that the row names are
carried forward to the bits element and can therefore be used to link the
subtype information with the rest of the patient data. The dataset contains
simulated cases where the category is undefined or the data are contaminated.
These are excluded from training.

If necessary, Allspice also allows overlapping categories, but then the
bits need to be supplied in a binary matrix where 1s indicate category
membership (the name of a column is the name of the corresponding category).
Samples should be organized into rows similarly to the covariates.

In the final step, the materials are assembled into the final classification
asset:

``` {r}
# Assemble the classification asset.
bALL <- asset()
assemble(bALL) <- materials
```

Since we excluded the category labels of "bad" samples, the training set
includes a subset of all samples. Categories that are too small (too few
samples) are ignored and will produce a warning. It is good practice to
prepare your dataset in such a way that all categories have at least
five members.

``` {r}
# Save asset to disk.
tpath <- tempfile()
export(bALL, folder = tpath)
```

The asset can now be loaded into a classifier:

``` {r}
# Create a classifier.
clstest <- classifier(tpath)
```

``` {r}
# Classify samples.
simutest <- bcellALL(5)
covariates(clstest) <- simutest$metadata
profiles(clstest) <- simutest$counts
primtest <- predictions(clstest)[[1]]
print(primtest[,c("LABEL","MATCH","FREQ","PROX","EXCL")])
```

``` {r}
# Show correct subtypes.
print(simutest$metadata)
```

Please use the tabs at the top to navigate to the next page.

## Iris data

Base R containts the classic Iris dataset that is attributed to Edgar
Anderson who collected it and Ronald Fisher who used it as an example of
linear discriminant analysis:


``` {r}
# Iris flower dataset.
print(head(iris))
```

To create a classification asset, it is good to make sure that the data are
properly identified:

``` {r}
# Set row names.
flowers <- iris
rownames(flowers) <- paste0("flower", 1:nrow(flowers))
print(flowers[c(1,80,150),])
```

The training dataset can now be finalized (note the format of the data
matrix):

``` {r}
# Prepare training set.
materials <- list(title="Iris species")
materials$dat <- t(flowers[,1:4]) # vars on rows, samples on columns
materials$bits <- flowers[,"Species",drop=FALSE]
```

The original species labels are short, however, it is nice to have the
full species names in the results as well. Adding labels can be accomplished
by

``` {r}
# Set human-readable category labels.
model <- asset()
labels <- c("Iris Setosa", "Iris Virginica", "Iris Versicolor")
names(labels) <- c("setosa", "virginica", "versicolor")
visuals(model) <- labels
```

Next, the RNA-seq normalization and logarithm needs to be disabled since this
is not RNA-seq data:

``` {r}
# Configure a new asset.
configuration(model) <- c(norm=FALSE, logarithm=FALSE)
configuration(model) <- c(nonzero.min=0, nonzero.ratio=0)
print(configuration(model))
```

The asset can now be finished

``` {r}
# Assemble the classification asset.
assemble(model) <- materials
tpath <- tempfile()
export(model, folder = tpath)
```
and tested:

``` {r}
# Classify samples.
clsiris <- classifier(tpath)
profiles(clsiris) <- t(flowers[,1:4])
iristest <- predictions(clsiris)[[1]]
print(iristest[c(1,80,150),c("LABEL","MATCH","PROX","EXCL")])
```

We know that the Setosa species is easiest to distinguish of the three
(see e.g. the Wikipedia page on the Iris study) and this is manifested
as an increase in ambiguous results for the two other categories:

``` {r}
# Summary of results.
print(table(iristest$LABEL, flowers$Species))
```

Please use the tabs at the top to navigate to the next page.

## Supercategories

On the previous tab, we changed the labels of the categories. It is also
possible to set duplicated labels, indeed, the default classifier contains
a tissue detection asset where the B-cell ALL covers multiple ALL
subtype centroids. Let's revisit the ALL classifier:

``` {r results="hide"}
# Default ALL classifier.
cls <- classifier()
```

``` {r}
# Predict source tissue.
simu <- bcellALL(5)
covariates(cls) <- simu$metadata
profiles(cls) <- simu$counts
tissues <- predictions(cls)[[3]]
print(tissues[,c("LABEL","CATEG","MATCH","MATCH.2nd")])
```

Notice how the predicted categories are different ALL subtypes, but the label
for every one of them is "B-cell ALL". In the visual report, only the
supercategory is displayed (see the figures in the section on sample
classification). The output also shows the second best matching category,
which in this case is the T-cell ALL RNA centroid. This is expected,
since it is another similar form of leukemia.

Why would you use labels to define these supercategories? The answer is a
technical one. You could put all the ALL samples together and calculate
a single B-cell ALL centroid, however, this model would be at risk of being
too coarse considering the great diversity of RNA profiles associated with
specific subtypes. For example, the rare but distinctive subtype driven by
the N159Y alteration in IKZF1 could be considered an outlier as it is far
from the overall ALL centroid, and thus these samples could be
incorrectly classified if the IKZF1 N159Y was not defined as
an explicit subtype.

## Asset contents

Classification assets are stored as text files on the disk and, although
not recommended, it is possible to view and edit them directly. For instance,
the files for ALL subtypes that were imported into the default classifier
can be found via system files that are part of the R library:

``` {r}
# Show asset contents.
base <- system.file(package = "Allspice")
folder <- file.path(base, "subtypes")
print(dir(folder))
```

**Categories** file contains information on the subtypes and their visual
attributes:

``` {r}
# Category information.
dat <- read.delim(file.path(folder, "categories.txt"))
print(dat)
```

**Centroids** file contains subtype profiles for pre-processed data values:

``` {r}
# Standardized subtype profiles.
dat <- read.delim(file.path(folder, "centroids.txt"))
print(dat[1:5,1:6])
cat(nrow(dat), " genes, ", ncol(dat), " subtypes\n", sep="")
```

**Coefficients** file contains the parameters for the back-end regression
analysis that combines the RNA biomarker from the centroid model with
the covariates. B0 is the intercept and B1 is the coefficient for the RNA
biomarker. Note that the coefficients depend on the scale of the inputs
(covariates are never standardized):

``` {r}
# Regression coefficients.
dat <- read.delim(file.path(folder, "coefficients.txt"))
print(dat[1:5,])
```

**Configuration** file contains the settings to determine how data
should be processed:

``` {r}
# Asset settings.
dat <- read.delim(file.path(folder, "configuration.txt"))
print(dat)
```

**Covariates** file contains the basic statistics of the covariates.
The MEAN is used as replacements for missing values:

``` {r}
# Covariate statistics.
dat <- read.delim(file.path(folder, "covariates.txt"))
print(dat)
```

**Nomenclature** file contains a dictionary for converting gene names
from one system to another. In this example, the asset uses Hugo symbols
but can translate ENSEMBL gene names as well:

``` {r}
# Gene names.
dat <- read.delim(file.path(folder, "nomenclature.txt"))
print(dat[1:5,])
```

**Reference** file contains basic statistics of the RNA-seq training data.
Only genes that are usable under the asset settings are included. The VALUE
column is the median of original values, whereas the mean and standard
deviation are calculated from the logarithms if the asset is so configured:

``` {r}
# RNA reference profile.
dat <- read.delim(file.path(folder, "reference.txt"))
print(dat[1:5,])
cat(nrow(dat), " genes\n", sep="")
```


# Build information

```{r echo=FALSE}
sessionInfo()
Sys.time()
```

``` {r echo=FALSE, results="hide"}
options(opt)
```
