---
title: "Advanced basketball statistics in R"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Advanced basketball statistics in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(AdvancedBasketballStats)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Advanced basketball statistics is an R package that allows you to perform different statistics calculations that are used in the world of basketball. In the package we can perform different calculations for the following types of statistics:

* Calculations on a data set representing individual statistics.
* Calculations on a data set representing lineup statistics.
* Calculations on a data set representing play statistics.
* Calculations on a data set representing team statistics.

# Data set

To create our data set we can do it in two different ways:

After deciding how to create our data set we must know what analysis we want to perform, since depending on this we will need different types of data sets:

1. We can use the functions that allow the transformation of a simple data set, that is, without the calculations performed by the data_adjustment() functions. The functions that the transformation allows are the following:
    + individuals_data_adjustment. Function that allows transformation of individual stats and defensive stats.
    + lineups_data_adjustment. Function that allows the transformation of lineups.
    + play_data_adjustment. Function that allows the transformation of plays.
    + team_stats. Function that allows you to perform team statistics.
    
2. We can use Data frames with the format corresponding to the data_adjustment() functions.

Once the two ways of creating the data have been commented, the examples of the data sets for subsequent use are shown:

## Individual Data Set
If we want to perform the analysis of individual statistics, we must have the following data sets:

* Data set that represents individual statistics.
  + Data set created the individuals_data_adjustment function:
    ```{r}
    individual_stats <- data.frame("Name" = c("James","Team"), "G" = c(67,0), 
    "GS" = c(62,0),"MP" = c(2316,1), "FG" = c(643,0), "FGA" = c(1303,0),
    "3P  " = c(148,0),"3PA" = c(425,0),"2P" = c(495,0), "2PA" = c(878,0),
    "FT" = c(264,0),"FTA" = c(381,0),"ORB" = c(66,0),  "DRB" = c(459,0),
    "AST" = c(684,0),"STL" = c(78,0),  "BLK" = c(36,0),"TOV" = c(261,0), 
    "PF" = c(118,0),"PTS" = c(1698,0),  "+/-" = c(0,0))
      
    individual_stats <- individuals_data_adjustment(individual_stats)
    individual_stats
    ```      
  + Data set created with the same structure as the one generated by the individuals_data_adjustment function
    ```{r}
    individual  <- data.frame("name" = c("LeBron James","Team"),"G" = c(67,0),
    "GS" = c(62,0),"MP" = c(2316,0),"FG" = c(643,0), "FGA" = c(1303,0),
    "Percentage FG" = c(0.493,0),"3P" = c(148,0),"3PA" = c(425,0),
    "Percentage 3P" = c(0.348,0),"2P" = c(495,0),"2PA" = c(878,0),
    "Percentage 2P" = c(0.564,0),"FT" = c(264,0),"FTA FG" = c(381,0),
    "Percentage FT" = c(0.693,0), "ORB" = c(66,0),"DRB" = c(459,0),
    "TRB" = c(525,0),"AST" = c(684,0),"STL" = c(78,0),"BLK" = c(36,0),
    "TOV" = c(261,0), "PF" = c(118,0),"PTS" = c(1698,0),"+/-" = c(0,0))
    
    individual
    ```
* Data set representing individual defensive statistics.
    + Data set created with the individuals_data_adjustment function:
    ```{r}
    defensive_stats <- data.frame("Name" = c("Witherspoon ","Team"), 
    "MP" = c(14,200),"DREB" = c(1,0),"FM" = c(4,0), "BLK" = c(0,0),
    "FTO" = c(0,0),"STL" = c(1,1), "FFTA" = c(0,0),  "DFGM" = c(1,0),
    "DFTM" = c(0,0))
    
    defensive_stats <- individuals_data_adjustment(defensive_stats)
    defensive_stats
    ```    
    + Data set created with the same structure as the one generated by the individuals_data_adjustment function
    ```{r}
    defensive <- data.frame("Name" = c("Witherspoon ","Team"), 
    "MP" = c(14,200),"DREB" = c(1,0), "FM" = c(4,0),
    "BLK" = c(0,0),"TOTAL FM" = c(4,0),"FTO" = c(0,0),
    "STL" = c(1,1), "TOTAL FTO " = c(1,0), "FFTA" = c(0,0),
    "DFGM" = c(1,0), "DFTM" = c(0,0))
    
    defensive
    ```    

* Data set that represents team statistics.
    + Data set created with the team_stats function:
    ```{r}
    tm_stats <- team_stats(individual_stats)
    tm_stats
    ```
    + Data set created with the same structure as the one generated by the team_stats function
    ```{r}
    indi_team_stats <- data.frame("G" = c(71), "MP" = c(17090), 
    "FG" = c(3006), "FGA" = c(6269),"Percentage FG" = c(0.48),
    "3P" = c(782),"3PA" = c(2242), "Percentage 3P" = c(0.349),
    "2P" = c(2224), "2PA" = c(4027), "Percentage 2P" = c(0.552),
    "FT" = c(1260),"FTA FG" = c(1728),"Percentage FT" = c(0.729),
    "ORB" = c(757),"DRB" = c(2490),"TRB" = c(3247),"AST" = c(1803),
    "STL" = c(612), "BLK" = c(468),"TOV" = c(1077),"PF" = c(1471), 
    "PTS" = c(8054),  "+/-" = c(0))
    
    indi_team_stats    
    ```    
* Data set that represents the statistics of the rival team.
    + Data set created with the same structure as the one generated by the team_stats function
    ```{r}
    indi_rival_stats <- data.frame("G" = c(71), "MP" = c(17090), 
    "FG" = c(2773), "FGA" = c(6187),"Percentage FG" = c(0.448),
    "3P" = c(827),"3PA" = c(2373),"Percentage 3P" = c(0.349),
    "2P" = c(1946), "2PA" = c(3814),"Percentage 2P" = c(0.510),
    "FT" = c(1270),"FTA FG" = c(1626),"Percentage FT" = c(0.781),
    "ORB" = c(668), "DRB" = c(2333),"TRB" = c(3001), "AST" = c(1662), 
    "STL" = c(585),"BLK" = c(263),"TOV" = c(1130),"PF" = c(1544),
    "PTS" = c(7643),  "+/-" = c(0))
    
    indi_rival_stats
    ```

## Lineup Data Set
If we want to perform the analysis of lineup statistics, we must have the following data sets:

* Data set that represents basic lineup statistics.
    + Data set created with the lineups_data_adjustment function
    ```{r}
    linp_basic <- data.frame("PG"= c("James","Rondo"),"SG" = c("Green","Caruso"),
    "SF" = c("Caldwell","Kuzma"), "PF" = c("Davis","Davis"),
    "C" = c("Howard ","Howard"),"MP" = c(7,1), "FG " = c(4,0),
    "FGA"  = c(7,0), "X3P" = c(0,0),"X3PA" = c(2,0),"X2P" = c(4,0),
    "X2PA" = c(5,0),  "FT" = c(1,0), "FTA" = c(3,0),"ORB" = c(2,0),
    "DRB" = c(5,0), "AST " = c(2,0), "STL " = c(1,0), "BLK " = c(0,0),
    "TOV " = c(7,2), "PF" = c(1,0),  "PLUS" = c(9,0),"MINUS" = c(17,3))
    
    linp_basic <- lineups_data_adjustment(linp_basic)
    linp_basic
    ```    
    + Data set created with the same structure as the one generated by the lineups_data_adjustment function
    ```{r}
    lineup_basic <- data.frame("PG" = c("James","Rondo"),"SG" = c("Green","Caruso"),
    "SF" = c("Caldwell","Kuzma"), "PF" = c("Davis","Davis"),
    "C" = c("Howard ","Howard"),"MP" = c(7,1), "FG " = c(4,0),
    "FGA " = c(7,0),"Percentage FG" = c(0.571,0),
    "X3P  " = c(0,0),"X3PA  " = c(2,0),"Percentage 3P" = c(0,0),
    "X2P " = c(4,0), "X2PA " = c(5,0), "Percentage 2P" = c(0.8,0),
    "FT " = c(1,0), "FTA " = c(3,0), "Percentage FT" = c(0.333,0),
    "ORB " = c(2,0), "DRB " = c(5,0),"TRB " = c(7,0), "AST " = c(2,0),
    "STL " = c(1,0), "BLK " = c(0,0),"TOV " = c(7,2), "PF" = c(1,0),
    "PLUS" = c(9,0),"MINUS" = c(17,3),"P/M" = c(-8,-3))
    
    lineup_basic
    ```    
* Data set that represents extended lineup statistics.
    + Data set created with the lineups_data_adjustment function
    ```{r}
    linp_extended <-  data.frame("PG" = c("James","Rondo"),"SG"= c("Green","Caruso"),
    "SF" = c("Caldwell","Kuzma"), "PF" = c("Davis","Davis"),
    "C" = c("Howard ","Howard"),"MP" = c(7,1), "FG " = c(6,0),
    "OppFG " = c(6,0), "FGA " = c(10,0),"OppFGA " = c(9,0),
    "X3P  " = c(2,0),"Opp3P  " = c(1,0),"X3PA " = c(4,0),
    "Opp3PA " = c(3,0),"X2P" = c(4,0),"Opp2P" = c(5,0),"X2PA " = c(6,0),
    "Opp2PA" = c(8,0) , "FT " = c(0,0),"OppFT " = c(1,0), "FTA " = c(0,0),
    "OppFTA" = c(1,0),"OppRB" = c(2,0),"OppOppRB" = c(1,0),"DRB" = c(4,0),
    "OppDRB" = c(1,0),"AST " = c(5,0),"OppAST " = c(4,0),"STL" = c(1,0),
    "OppSTL" = c(3,0),"BLK" = c(0,0),"OppBLK" = c(1,0),"TOppV" = c(5,2),
    "OppTOppV" = c(3,2),"PF" = c(1,0),"OppPF" = c(3,0),"PLUS" = c(15,0),
    "MINUS" = c(14,3))
    
    linp_extended <- lineups_data_adjustment(linp_extended)
    linp_extended
    ```    
    + Data set created with the same structure as the one generated by the lineups_data_adjustment function
    ```{r}
    lineup_extended <-  data.frame("PG" = c("James","Rondo"),"SG" = c("Green","Caruso"),
    "SF" = c("Caldwell","Kuzma"), "PF" = c("Davis","Davis"),
    "C" = c("Howard ","Howard"),"MP" = c(7,1), "FG " = c(6,0),
    "OppFG " = c(6,0), "FGA " = c(10,0),"OppFGA " = c(9,0),
    "X3P  " = c(2,0),"Opp3P" = c(1,0),"X3PA" = c(4,0),"Opp3PA" = c(3,0),
    "X2P" = c(4,0),"Opp2P " = c(5,0), "X2PA " = c(6,0),"Opp2PA " = c(8,0) ,
    "FT " = c(0,0),"OppFT " = c(1,0), "FTA " = c(0,0),"OppFTA " = c(1,0),
    "OppRB " = c(2,0),"OppOppRB " = c(1,0), "DRB" = c(4,0),"OppDRB" = c(1,0),
    "TRB" = c(6,0),"OppTRB" = c(2,0), "AST " = c(5,0),"OppAST " = c(4,0),
    "STL " = c(1,0),"OppSTL " = c(3,0), "BLK " = c(0,0),  "OppBLK " = c(1,0),
    "TOppV " = c(5,2), "OppTOppV " = c(3,2),"PF" = c(1,0),"OppPF" = c(3,0),
    "PLUS" = c(15,0),"MINUS" = c(14,3),"P/M" = c(1,-3))
    
    lineup_extended
    ```    

* Data set that represents team statistics.
    + Data set created with the team_stats function:
    ```{r}
    tm_stats <- team_stats(individual_stats)
    tm_stats
    ```
    + Data set created with the same structure as the one generated by the team_stats function
    ```{r}
    lineup_team_stats <- data.frame("G" = c(71), "MP" = c(17090),
     "FG" = c(3006), "FGA" = c(6269),"Percentage FG" = c(0.48),
     "3P" = c(782),"3PA" = c(2242), "Percentage 3P" = c(0.349),
    "2P" = c(2224), "2PA" = c(4027), "Percentage 2P" = c(0.552),
    "FT" = c(1260),"FTA FG" = c(1728),  "Percentage FT" = c(0.729),
    "ORB" = c(757), "DRB" = c(2490),"TRB" = c(3247),"AST" = c(1803), 
    "STL" = c(612),  "BLK" = c(468),"TOV" = c(1077),"PF" = c(1471),  
    "PTS" = c(8054),  "+/-" = c(0))
    
    lineup_team_stats    
    ```    
* Data set that represents the statistics of the rival team.
    ```{r}
    lineup_rival_stats <- data.frame("G" = c(71), "MP" = c(17090),
    "FG" = c(2773), "FGA" = c(6187),"Percentage FG" = c(0.448),
    "3P" = c(827),"3PA" = c(2373),"Percentage 3P" = c(0.349),
    "2P" = c(1946), "2PA" = c(3814),"Percentage 2P" = c(0.510), 
    "FT" = c(1270),"FTA FG" = c(1626),  "Percentage FT" = c(0.781),
    "ORB" = c(668), "DRB" = c(2333),"TRB" = c(3001), "AST" = c(1662), 
    "STL" = c(585),"BLK" = c(263),"TOV" = c(1130),"PF" = c(1544), 
    "PTS" = c(7643),  "+/-" = c(0))
    
    lineup_rival_stats
    ```  

## Play Data Set
If we want to perform the analysis of play statistics, we must have the following data sets:

* Data set that represents play statistics.
    + Data set created with the play_data_adjustment function
    ```{r}
    play_stats <- data.frame("Name" = c("Sabonis ","Team"), 
    "GP" = c(62,71),"PTS" = c(387,0), "FG" = c(155,1),
    "FGA" = c(281,1),"3P" = c(6,1),"3PA" = c(18,1),
    "FT" = c(39,1),  "FTA" = c(53,1),"ANDONE" = c(12,1),
    "AST" = c(0,1), "TOV" = c(27,1))
    
    play_stats <- play_data_adjustment(play_stats)
    play_stats
    ```    
    + Data set created with the same structure as the one generated by the play_data_adjustment function
    ```{r}
    play <- data.frame("Name" = c("Sabonis ","Team"),
    "GP" = c(62,71),"PTS" = c(387,0), "FG" = c(155,1),
    "FGA" = c(281,1),"3P" = c(6,1),"3PA" = c(18,1), 
    "FT" = c(39,1), "FTA" = c(53,1),"ANDONE" = c(12,1),
    "AST" = c(0,1), "TOV" = c(27,1))
    
    play
    ```    
* Data set that represents team statistics.
    + Data set created with the team_stats function:
    ```{r}
    tm_stats <- team_stats(individual_stats)
    tm_stats
    ```
    + Data set created with the same structure as the one generated by the team_stats function
    ```{r}
    play_team_stats <- data.frame("G" = c(71), "MP" = c(17090),
    "FG" = c(3006), "FGA" = c(6269),"Percentage FG" = c(0.48),
    "3P" = c(782),"3PA" = c(2242), "Percentage 3P" = c(0.349),
    "2P" = c(2224), "2PA" = c(4027), "Percentage 2P" = c(0.552),
    "FT" = c(1260),"FTA FG" = c(1728),  "Percentage FT" = c(0.729),
    "ORB" = c(757),"DRB" = c(2490),"TRB" = c(3247),"AST" = c(1803),
    "STL" = c(612), "BLK" = c(468),"TOV" = c(1077),"PF" = c(1471), 
    "PTS" = c(8054),  "+/-" = c(0))
    
    play_team_stats    
    ```    
    + Data set that represents the statistics of the rival team.
    ```{r}
    play_rival_stats <- data.frame("G" = c(71), "MP" = c(17090),
    "FG" = c(2773), "FGA" = c(6187),"Percentage FG" = c(0.448),
    "3P" = c(827),"3PA" = c(2373),"Percentage 3P" = c(0.349),
    "2P" = c(1946), "2PA" = c(3814),"Percentage 2P" = c(0.510),
    "FT" = c(1270),"FTA FG" = c(1626),"Percentage FT" = c(0.781),
    "ORB" = c(668),"DRB" = c(2333),"TRB" = c(3001),"AST" = c(1662),
    "STL" = c(585),"BLK" = c(263),"TOV" = c(1130),"PF" = c(1544),
    "PTS" = c(7643),  "+/-" = c(0))
    
    play_rival_stats
    ```    

## Team Data Set  
If we want to perform the analysis of team statistics, we must have the following data sets:

* Data set that represents the statistics of the team. 

    + Data set created with the team_stats function:
    ```{r}
    tm_stats <- team_stats(individual_stats)
    tm_stats
    ```
    + Data set created with the same structure as the one generated by the team_stats function
    ```{r}
    team_stats <- data.frame("G" = c(71), "MP" = c(17090),
    "FG" = c(3006), "FGA" = c(6269),"Percentage FG" = c(0.48),
    "3P" = c(782),"3PA" = c(2242), "Percentage 3P" = c(0.349),
    "2P" = c(2224), "2PA" = c(4027),"Percentage 2P" = c(0.552),
    "FT" = c(1260),"FTA FG" = c(1728),"Percentage FT" = c(0.729),
    "ORB" = c(757),"DRB" = c(2490),"TRB" = c(3247),"AST" = c(1803),
    "STL" = c(612),"BLK" = c(468),"TOV" = c(1077),"PF" = c(1471),
    "PTS" = c(8054),  "+/-" = c(0))
    
    team_stats    
    ```    
* Data set that represents the statistics of the rival team.
    ```{r}
    rival_stats <- data.frame("G" = c(71), "MP" = c(17090), 
    "FG" = c(2773), "FGA" = c(6187),"Percentage FG" = c(0.448),
    "3P" = c(827),"3PA" = c(2373),"Percentage 3P" = c(0.349),
    "2P" = c(1946), "2PA" = c(3814),"Percentage 2P" = c(0.510),
    "FT" = c(1270),"FTA FG" = c(1626),"Percentage FT" = c(0.781),
    "ORB" = c(668),"DRB" = c(2333),"TRB" = c(3001),"AST" = c(1662),
    "STL" = c(585),"BLK" = c(263),"TOV" = c(1130),"PF" = c(1544),
    "PTS" = c(7643),  "+/-" = c(0))
    
    rival_stats
    ```  

Once the data sets have been created, we must choose which function or functions we want to use. Below are the different functions that the package has:

# Functions for individual statistics

For individual statistics there are the following functions:

* __individuals_advance_stats.__ Function that allows advanced statistics calculation.
* __individuals_defensive_actual_floor_stats.__ Function that allows the calculation of the current defensive statistics.
* __individuals_defensive_estimated_floor_stats.__ Function that allows the calculation of the estimated defensive statistics.
* __individuals_games_adder.__ Function that allows the sum of two different individual statistics.
* __individuals_ofensive_floor_stats.__ Function that allows the calculation of offensive statistics.
* __individuals_stats_per_game.__ Function that allows the calculation of statistics per game.
* __individuals_stats_per_minutes.__ Function that allows the calculation of statistics per minutes.
* __individuals_stats_per_possesion.__ Function that allows the calculation of statistics per possessions.

Below is an example of how each function works and what the input parameters should be for these:

## individuals_advance_stats
For this function we will have to enter individual statistics, team statistics and rival team statistics:

```{r}
advanced_stats <- individuals_advance_stats(individual,indi_team_stats,indi_rival_stats)
advanced_stats
```

## individuals_defensive_actual_floor_stats
For this function we will have to enter defensive individual statistics, team statistics and rival team statistics:
```{r}
defensive_actual_stats <- individuals_defensive_actual_floor_stats(defensive,indi_team_stats,indi_rival_stats)
defensive_actual_stats
```
## individuals_defensive_estimated_floor_stats
For this function we will have to enter individual statistics, team statistics and rival team statistics:
```{r}
defensive_estimated_stats <- individuals_defensive_estimated_floor_stats(individual,indi_team_stats,indi_rival_stats)
defensive_estimated_stats
```
## individuals_games_adder. 
For this function we will have to enter the two individual statistics previously calculated which we want to add the statistics:
```{r}
games_adder <- individuals_games_adder(individual,individual)
games_adder
```
## individuals_ofensive_floor_stats. 
For this function we will have to enter individual statistics, team statistics and rival team statistics:
```{r}
ofensive_stats <- individuals_ofensive_floor_stats(individual,indi_team_stats,indi_rival_stats)
ofensive_stats
```
## individuals_stats_per_game
For this function we will have to enter individual statistics:
```{r}
per_game_stats <- individuals_stats_per_game(individual)
per_game_stats
```
## individuals_stats_per_minutes
For this function we will have to enter the individual statistics and the number of minutes to which we want to project the statistics:
```{r}
per_minutes_stats <- individuals_stats_per_minutes(individual,36)
per_minutes_stats
```
## individuals_stats_per_possesion
For this function we will have to enter the individual statistics, the team statistics, the rival team statistics, the number of minutes that a single game lasts and the number of possessions to which we want to project the statistics:
```{r}
per_poss_stats <- individuals_stats_per_possesion(individual,indi_team_stats,indi_rival_stats,100,48)
per_poss_stats
```

# Functions for lineup statistics

For individual statistics there are the following functions:

* __lineups_advance_stats.__ Function that allows advanced statistics calculation.
* __lineups_backcourt.__ Function that allows searching for backcourt players.
* __lineups_comparator_stats.__ Function that allows comparison between the statistics of the lineup and the rival lineup
* __lineups_games_adder.__ Function that allows the sum of two different lineup statistics.
* __lineups_paint.__ Function that allows searching for paint players.
* __lineups_players.__ Function that allows searching for players by position.
* __lineups_searcher.__ Function that allows searching for players within the data frame.
* __lineups_separator.__ Function that allows you to obtain the statistics of the lineups or the rivals against those lineups.
* __lineups_stats_per_possesion.__ Function that allows the calculation of statistics per possessions

Below is an example of how each function works and what the input parameters should be for these:


## lineups_advance_stats

For this function we will have to enter extended lineup statistics and the number of minutes that a single game lasts:

```{r}
lnp_advanced_stats <- lineups_advance_stats(lineup_extended,48)
lnp_advanced_stats
```

## lineups_backcourt

For this function we will have to enter basic lineup statistics or extended lineup statistics:

```{r}
lnp_bs_backcourt <- lineups_backcourt(lineup_basic)
lnp_bs_backcourt
```

```{r}
lnp_ex_backcourt <- lineups_backcourt(lineup_extended)
lnp_ex_backcourt
```
## lineups_comparator_stats

For this function we will have to enter extended lineup statistics:

```{r}
lnp_comparator <- lineups_comparator_stats(lineup_extended,48)
lnp_comparator
```

## lineups_games_adder

For this function we will have to enter basic lineup statistics or extended lineup statistics:
```{r}
lnp_games_adder <- lineups_games_adder(lineup_basic,lineup_basic)
lnp_games_adder
```

## lineups_paint

For this function we will have to enter basic lineup statistics or extended lineup statistics:

```{r}
lnp_bc_paint <- lineups_paint(lineup_basic)
lnp_bc_paint
```

```{r}
lnp_ex_paint <- lineups_paint(lineup_extended)
lnp_ex_paint
```

## lineups_players

For this function we will have to enter basic lineup statistics or extended lineup statistics and the number of position that we want to find:

```{r}
lnp_bc_players <- lineups_players(lineup_basic,5)
lnp_bc_players
```

```{r}
lnp_ex_players <- lineups_players(lineup_extended,5)
lnp_ex_players
```

## lineups_searcher

For this function we will have to enter basic lineup statistics or extended lineup statistics, the name of the players that we want to find and the number of players that we want to find:

```{r}
lnp_bc_searcher <- lineups_searcher(lineup_basic,1,"James","","","")
lnp_bc_searcher
```

```{r}
lnp_ex_searcher <- lineups_searcher(lineup_extended,1,"James","","","")
lnp_ex_searcher
```


## lineups_separator

For this function we will have to enter extended lineup statistics and the indicator of what type of separation we want to make:

```{r}
lnp_ex_sep_one <- lineups_separator(lineup_extended,1)
lnp_ex_sep_one
```

```{r}
lnp_ex_sep_two <- lineups_separator(lineup_extended,2)
lnp_ex_sep_two
```

## lineups_stats_per_possesion

For this function we will have to enter basic lineup statistics, team statistics, rival team statistics, the number of minutes that a single game lasts and the number of possessions to which we want to project the statistics:

```{r}
lnp_per_poss_stats <- lineups_stats_per_possesion(lineup_basic,lineup_team_stats,lineup_rival_stats,100,48)
lnp_per_poss_stats
```


# Functions for play statistics

For individual statistics there are the following functions:

* __play_advance_stats.__ Function that allows advanced statistics calculation.
* __play_games_adder.__ Function that allows the sum of two different play statistics.
* __play_stats_per_game.__ Function that allows the calculation of statistics per game.
* __play_stats_per_possesion.__ Function that allows the calculation of statistics per possessions.
* __play_team_stats.__ Function that allows to carry out the statistics of the team.

Below is an example of how each function works and what the input parameters should be for these:

## play_advance_stats

For this function we will have to enter play statistics:
```{r}
play_adv_stats <- play_advance_stats(play_stats)
play_adv_stats
```

## play_games_adder

For this function we will have to enter play statistics:

```{r}
pl_game_adder <- play_games_adder(play_stats,play_stats)
pl_game_adder
```

## play_stats_per_game

For this function we will have to enter play statistics:

```{r}
play_per_game_stat <- play_stats_per_game(play_stats)
play_per_game_stat
```

## play_stats_per_possesion

For this function we will have to enter the play statistics, the team statistics, the rival team statistics, the number of minutes that a single game lasts and the number of possessions to which we want to project the statistics:

```{r}
play_per_poss_stats <- play_stats_per_possesion(play_stats,play_team_stats,play_rival_stats,100,48)
play_per_poss_stats
```

## play_team_stats

For this function we will have to enter play statistics:

```{r}
play_team_stats <- play_team_stats(play_stats)
play_team_stats
```


# Functions for team statistics

For individual statistics there are the following functions:

* __team_advanced_stats.__ Function that allows advanced statistics calculation.
* __team_stats_per_game.__ Function that allows the calculation of statistics per game.
* __team_stats_per_minutes.__ Function that allows the calculation of statistics per minutes.
* __team_stats_per_possesion.__ Function that allows the calculation of statistics per possessions.

Below is an example of how each function works and what the input parameters should be for these:

## team_advanced_stats

For this function we will have to enter the team statistics and the rival team statistics:

```{r}
team_adv_stats  <- team_advanced_stats(team_stats,rival_stats,48)
team_adv_stats
```

## team_stats_per_game

For this function we will have to enter the team statistics:

```{r}
team_per_game_stat <- team_stats_per_game(team_stats)
team_per_game_stat
```

## team_stats_per_minutes

For this function we will have to enter the team statistics and the number of minutes to which we want to project the statistics:

```{r}
team_per_minutes_stat <- team_stats_per_minutes(team_stats,36)
team_per_minutes_stat
```

## team_stats_per_possesion

For this function we will have to enter the team statistics, the rival team statistics and the number of possessions to which we want to project the statistics::

```{r}
team_per_poss_stat <- team_stats_per_possesion(team_stats,rival_stats,100)
team_per_poss_stat
```

